### 2014-12-08 paper.tex
Initial paper outline
Contents of SIPWork poster copied in as a starting point for the paper.

\documentclass{article}
\begin{document}

\section{Introduction}
Few studies have investigated how the temperatures of flaring active regions behave prior to the flare.
This method tracks flaring active regions and visualises their long-term temperature distribution.
We attempt to find signatures of flares in the temperature profiles of active regions, which might be used for flare prediction.
This method uses SunPy, a free, open-source Python library for solar physics.

\section{Method}
This study uses a temperature map method similar to that of [1] to calculate coronal temperatures by comparing the relative brightnesses in the different AIA wavelengths.
Active regions AR11138-AR11183 are studied.
The location and duration of each active region is obtained from the Heliophysics Events Knowledgebase (HEK).
Using this information, a temperature map is calculated for a 50x50 arcsec area around each active region at 2-hour intervals from two days before the active region emerges or rotates into view until two days after it has dissipated or rotated out of view.
How the temperature distribution changes with time is then compared to when associated flares occur for each active region.
The flares associated with these regions have also been investigated individually.
Information for each flare was again found by querying the HEK.
For each flare the 95th percentile temperature was calculated from one temperature map of the corresponding active region.
This map was chosen as the latest map before the start time of the flare.
All flares were then plotted on a scatter graph of this temperature against the peak GOES flux of the flare.

\section{Results}
Figures 1 and 2 show the mean, standard deviation, 95th percentile and maximum temperature of active regions AR11146 and AR11149 respectively, as functions of time.
The times of the associated flares are also plotted. These regions were chosen as they are typical of the results found for other active regions, and show similar temperature profiles but different numbers of flares. In both plots, some time before a flare or group of flares occur, the maximum temperature rises significantly but the bulk temperature of the region varies relatively little.
Figure 3 plots the peak flux for all flares associated with the studied active regions against the 95th percentile temperature for the corresponding active regions before the beginning of the flare.
Most of these flares are grouped around log(T) $\approx$ 6.35, 6.55 and 6.7, with fewer flares associated with hotter active regions, generally.
However, the strongest flares observed do appear to be associated with hotter active regions.

\section{Discussion}
Figures 1 and 2 show that there is no clear trend in the long-term temperature distribution before flares occur.
This is also the case for the other active regions investigated. If any trend in temperature does occur before large flares, it may be on a shorter timescale than investigated here, and may only be noticable for very large flares.
Any further work on this topic should therefore look at shorter timespans with higher cadence, and perhaps only consider active regions associated with X-class flares.
From figure 3 it can be seen that there does appear to be some grouping of flaring active regions into groups of temperatures, and that a few of the larger flares are associated with active regions at higher temperatures than most of the other flares investigated.
However, no clear correlation can be seen between peak flare flux and active region temperature.
A much larger sample of flares is needed in order to properly determine whether or not a link exists between the two.

\section{Conclusions}

\bibliographystyle{plainnat}
\bibliography{C:/Users/Drew/Dropbox/Thesis/thesis_refs,C:/Users/Drew/Documents/library}

\end{document}

### 2014-12-09 paper.tex
changes

@@
 \section{Method}
-This study uses a temperature map method similar to that of [1] to calculate coronal temperatures by comparing the relative brightnesses in the different AIA wavelengths.
-Active regions AR11138-AR11183 are studied.
-The location and duration of each active region is obtained from the Heliophysics Events Knowledgebase (HEK).
-Using this information, a temperature map is calculated for a 50x50 arcsec area around each active region at 2-hour intervals from two days before the active region emerges or rotates into view until two days after it has dissipated or rotated out of view.
+The core of this analysis is the temperature map method described by \cite{Leonard2014} (henceforth Paper I).
+Briefly, this method compares the relative brightnesses in each AIA wavelength channel at a given time and infers the best-fitting temperature from that comparison.
+This allows the temperature of the corona to be estimated for every pixel of an AIA image, resulting in very high resolution temperature maps.
+
+The method of Paper I was used to investigate the temperatures of flaring active regions betwen AR11138-AR11183. %subsitute dates here
+The Heliophysics Events Knowledgebase (HEK) was queried to find the location on the solar disk of each active region and the time of any flares associated with the regions.
+Using this information, a temperature map was calculated for a 50x50 arcsec area around each active region at 1-minute intervals for the hour preceding a flare event.
 How the temperature distribution changes with time is then compared to when associated flares occur for each active region.
-The flares associated with these regions have also been investigated individually.
-Information for each flare was again found by querying the HEK.
+The mean (and standard deviation? percentiles?) of the temperature map was calculated at each time step and these values were plotted for each flare.
+
+The overall behaviour of the active  region temperatures before flares was also investigated.
 For each flare the 95th percentile temperature was calculated from one temperature map of the corresponding active region.
-This map was chosen as the latest map before the start time of the flare.
+This map was chosen as the latest map before the start time of the flare. % was it?
 All flares were then plotted on a scatter graph of this temperature against the peak GOES flux of the flare.

### 2014-12-09 paper.tex
More detail and some structure

@@
 \documentclass{article}
+
+\author{Andrew Leonard and Huw Morgan}
+%\email{ajl7@aber.ac.uk}
+%\institution{Institute of Mathematics, Physics and Computer Science, Aberystwyth University, Ceredigion, SY23 3BZ, Wales}
+
+%\author{Huw Morgan}
+%\email{hum2@aber.ac.uk}
+%\institution{Institute of Mathematics, Physics and Computer Science, Aberystwyth University, Ceredigion, SY23 3BZ, Wales}
+
+\title{Using temperature distributions of active regions to investigate flare activity}
+
 \begin{document}
 
+\maketitle
+
+%===========================================================================
 \section{Introduction}
-Few studies have investigated how the temperatures of flaring active regions behave prior to the flare.
-This method tracks flaring active regions and visualises their long-term temperature distribution.
-We attempt to find signatures of flares in the temperature profiles of active regions, which might be used for flare prediction.
+Solar flares are a complicated and as yet not fully understood phenomenon.
+In particular, growing emphasis has been placed in recent years on studying how to predict when a flare will occur, since flares and associated coronal phenomena can have significant detrimental effects on a variety of modern electronic infrastructure.
+Many studies have been devoted to this topic, but few have looked at the temperature of the active regions associated with flares before the flare occurs.
+
+Studying the temperature of the corona is not a new pursuit, but for many years the data were significantly limited.
+Most imagers had either relatively poor spatial resolution or too few wavelength channels to effectively constrain temperature solutions, whereas spectrometers could provide very accurate temperatures but only over very small portions of the corona.
+Imagers and spectrometers also typically had insufficient temporal resolution to investigate any dynamic events in the corona.
+Recently, however, the very high temporal and spatial resolution of the Atmospheric Imaging Assembly (AIA) on the Solar Dynamics Observatory (SDO) allows us to investigate small-scale and dynamic events anywhere on the solar disk at any time.
+The six Fe-based EUV channels also provide sufficent constraints to allow a reasonable estimate of coronal temperatures.
+
+This work makes use of the capabilities of AIA in order to investigate the temperature distributions of several flaring active regions.
+The aim is to search for a common signature of flare activity in these temperature distributions before flares occur, which, if found, could form the basis of a flare prediction algorithm.
+To achieve this, we look at temperature distributions of the active regions over the hour before a flare occurs, and we also compare the temperatures of the corresponding active regions shortly before the flares.
+
 This method uses SunPy, a free, open-source Python library for solar physics.
 
+%===========================================================================
 \section{Method}
+\subsection{Temperature analysis}
 The core of this analysis is the temperature map method described by \cite{Leonard2014} (henceforth Paper I).
@@
 
-The method of Paper I was used to investigate the temperatures of flaring active regions betwen AR11138-AR11183. %subsitute dates here
-The Heliophysics Events Knowledgebase (HEK) was queried to find the location on the solar disk of each active region and the time of any flares associated with the regions.
-Using this information, a temperature map was calculated for a 50x50 arcsec area around each active region at 1-minute intervals for the hour preceding a flare event.
-How the temperature distribution changes with time is then compared to when associated flares occur for each active region.
+\subsection{Active region analysis}
+The method of Paper I was used to investigate the temperatures of flaring active regions betwen AR11138-AR11183. %substitute dates here
+The first part of the investigation tracked active regions as they moved across the solar disk and plotted their temperature distributions in the hour leading up to a flare.
+Then the temperatures of the associated active regions were directly compared for each of the investigated flares.
+
+\subsubsection{Long-term temperature distribution}
+For each flare event investigated, a temperature map was calculated for a 50x50 arcsec area around the corresponding active region at 1-minute intervals for the hour preceding the event.
+The times of the flares and the locations of the active regions on the solar disk were obtained by querying the Heliophysics Events Knowledgebase (HEK).
+How the temperature distribution changes with time was then compared to when associated flares occur for each active region.
 The mean (and standard deviation? percentiles?) of the temperature map was calculated at each time step and these values were plotted for each flare.
 
-The overall behaviour of the active  region temperatures before flares was also investigated.
+\subsubsection{Temperatures of active regions before flares}
 For each flare the 95th percentile temperature was calculated from one temperature map of the corresponding active region.
@@
 
+%===========================================================================
 \section{Results}
@@
 
+%===========================================================================
 \section{Discussion}
@@
 
+%===========================================================================
 \section{Conclusions}
 
+%===========================================================================
 \bibliographystyle{plainnat}

### 2014-12-09 paper.tex
More minor changes

@@
 \section{Discussion}
+
+\subsubsection{Long-term temperature distribution}
 Figures 1 and 2 show that there is no clear trend in the long-term temperature distribution before flares occur.
@@
 Any further work on this topic should therefore look at shorter timespans with higher cadence, and perhaps only consider active regions associated with X-class flares.
+
+\subsubsection{Temperatures of active regions before flares}
 From figure 3 it can be seen that there does appear to be some grouping of flaring active regions into groups of temperatures, and that a few of the larger flares are associated with active regions at higher temperatures than most of the other flares investigated.

### 2014-12-09 plotflares3.py
Rubbish version of analysis code added

@@ -1,0 +1,68 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Dec 09 18:15:45 2014
+
+@author: Drew Leonard
+"""
+
+from matplotlib import use
+use('agg')
+from sunpy import wcs
+from sunpy.map import Map
+from sunpy.net import hek
+from sunpy.time import parse_time as parse
+from sunpy.time.timerange import TimeRange as tr
+import datetime as dt
+from repeat_tempmaps import repeat
+from os.path import join
+
+start = parse('2011-02-10')
+end = parse('2011-02-16')
+#end = parse('2011-01-04')
+
+client = hek.HEKClient()
+flares = client.query(hek.attrs.Time(start, end),
+                      hek.attrs.EventType('FL'))
+
+flares = [fl for fl in flares if (fl['ar_noaanum'] > 11137 and 
+                                  fl['ar_noaanum'] < 11184)]
+
+fluxes = []
+temps = []
+coords = []
+datefile = open('dates.txt', 'w')
+datefile.write('')
+datefile.close()
+
+for flare in flares:
+    flaretime = parse(flare['event_starttime'])
+    starttime = flaretime-dt.timedelta(hours=0.5)
+    timerange = tr(starttime, flaretime)
+
+    fits_dir = '/imaps/sspfs/archive/sdo/aia/activeregions/'.format(starttime)
+    fname = 'aia*171*{0:%Y?%m?%d}?{0:%H?%M?%S}*lev1?fits'.format(flaretime)
+    filepath = join(fits_dir, fname)
+    temp_im = Map(filepath)
+    region = client.query(hek.attrs.EventType('AR'),
+                          hek.attrs.Time(flaretime-dt.timedelta(minutes=5), 
+                                         flaretime))
+    if flare['ar_noaanum'] == 11149:
+        print 'HEK is fucked, using 11147'
+        flare['ar_noaanum'] = 11147
+    region = [r for r in region if r['ar_noaanum'] == flare['ar_noaanum']]
+    if isinstance(region, list):
+        try:
+            region = region[0]
+        except IndexError:
+            continue
+    coords = wcs.convert_hg_hpc(region['hgc_x'], region['hgc_y'],
+                                b0_deg=temp_im.heliographic_latitude,
+                                l0_deg=temp_im.carrington_longitude)
+    
+    datefile = open('dates.txt', 'a')
+    datefile.write('\nAR{}; {}\n'.format(flare['ar_noaanum'],
[…]

### 2014-12-09 plotflares3.py
Updates to analysis code

@@ -8,17 +8,18 @@ Created on Tue Dec 09 18:15:45 2014
 from matplotlib import use
 use('agg')
 from sunpy import wcs
-from sunpy.map import Map
 from sunpy.net import hek
 from sunpy.time import parse_time as parse
 from sunpy.time.timerange import TimeRange as tr
 import datetime as dt
 from repeat_tempmaps import repeat
 from os.path import join
+from sys import path
+path.append('/imaps/holly/drew/CoronaTemps/')
+from temperature import TemperatureMap as tmap
 
 start = parse('2011-02-10')
-end = parse('2011-02-16')
-#end = parse('2011-01-04')
+end = parse('2011-04-01')
 
 client = hek.HEKClient()
 flares = client.query(hek.attrs.Time(start, end),
@@ -34,15 +35,13 @@ datefile = open('dates.txt', 'w')
 datefile.write('')
 datefile.close()
 
+ar_rad = 75
+
 for flare in flares:
     flaretime = parse(flare['event_starttime'])
     starttime = flaretime-dt.timedelta(hours=0.5)
     timerange = tr(starttime, flaretime)
 
-    fits_dir = '/imaps/sspfs/archive/sdo/aia/activeregions/'.format(starttime)
-    fname = 'aia*171*{0:%Y?%m?%d}?{0:%H?%M?%S}*lev1?fits'.format(flaretime)
-    filepath = join(fits_dir, fname)
-    temp_im = Map(filepath)
     region = client.query(hek.attrs.EventType('AR'),
                           hek.attrs.Time(flaretime-dt.timedelta(minutes=5), 
                                          flaretime))
@@ -55,14 +54,29 @@ for flare in flares:
             region = region[0]
         except IndexError:
             continue
-    coords = wcs.convert_hg_hpc(region['hgc_x'], region['hgc_y'],
-                                b0_deg=temp_im.heliographic_latitude,
-                                l0_deg=temp_im.carrington_longitude)
     
-    datefile = open('dates.txt', 'a')
-    datefile.write('\nAR{}; {}\n'.format(flare['ar_noaanum'],
-                                         flare['fl_goescls']))
-    datefile.close()
     means, fluxes, maxes, times = repeat(starttime, flaretime, timeres=1.0/60.0,
                                          coords=coords, ar=flare['ar_noaanum'], 
                                          plotminmax=True)
+    # Define times for maps
+    delta = dt.timedelta(minutes=1)
+    ntimes = int(timerange.seconds()/delta.total_seconds())
[…]

### 2014-12-10 plotflares3.py
Code adjusted for Huw's data structure

@@ -55,17 +55,18 @@ for flare in flares:
         except IndexError:
             continue
     
-    means, fluxes, maxes, times = repeat(starttime, flaretime, timeres=1.0/60.0,
-                                         coords=coords, ar=flare['ar_noaanum'], 
-                                         plotminmax=True)
     # Define times for maps
     delta = dt.timedelta(minutes=1)
     ntimes = int(timerange.seconds()/delta.total_seconds())
     times = [time.start() for time in timerange.split(ntimes)]
     
+    home = '/imaps/sspfs/archive/sdo/aia'
+    data_dir = join(home, 'activeregions/*/data/')
+    maps_dir = join(home, 'activeregions/*/images/')
+    
     for time in times:
         # Load/calculate temperature map data
-        thismap = tmap(time)
+        thismap = tmap(time, data_dir=data_dir, maps_dir=maps_dir)
         thismap.save()
         
         # Crop temperature map to active region

### 2014-12-10 plotflares3.py
Extraneous import statement removed

@@ -12,7 +12,6 @@ from sunpy.net import hek
 from sunpy.time import parse_time as parse
 from sunpy.time.timerange import TimeRange as tr
 import datetime as dt
-from repeat_tempmaps import repeat
 from os.path import join
 from sys import path
 path.append('/imaps/holly/drew/CoronaTemps/')

### 2014-12-10 plotflares3.py
temperature directory corrected

@@ -14,7 +14,7 @@ from sunpy.time.timerange import TimeRange as tr
 import datetime as dt
 from os.path import join
 from sys import path
-path.append('/imaps/holly/drew/CoronaTemps/')
+path.append('/imaps/holly/home/drew/CoronaTemps/')
 from temperature import TemperatureMap as tmap
 
 start = parse('2011-02-10')

### 2014-12-10 plotflares3.py
temperature directory actually corrected

@@ -14,7 +14,7 @@ from sunpy.time.timerange import TimeRange as tr
 import datetime as dt
 from os.path import join
 from sys import path
-path.append('/imaps/holly/home/drew/CoronaTemps/')
+path.append('/imaps/holly/home/ajl7/CoronaTemps/')
 from temperature import TemperatureMap as tmap
 
 start = parse('2011-02-10')

### 2014-12-10 plotflares3.py
data directories defined more specifically

@@ -60,8 +60,8 @@ for flare in flares:
     times = [time.start() for time in timerange.split(ntimes)]
     
     home = '/imaps/sspfs/archive/sdo/aia'
-    data_dir = join(home, 'activeregions/*/data/')
-    maps_dir = join(home, 'activeregions/*/images/')
+    data_dir = join(home, 'activeregions/AR11153/data/')
+    maps_dir = join(home, 'activeregions/AR11153/images/')
     
     for time in times:
         # Load/calculate temperature map data

### 2014-12-11 plotflares3.py
tempmap save dir changed again

@@ -59,9 +59,11 @@ for flare in flares:
     ntimes = int(timerange.seconds()/delta.total_seconds())
     times = [time.start() for time in timerange.split(ntimes)]
     
-    home = '/imaps/sspfs/archive/sdo/aia'
+    """home = '/imaps/sspfs/archive/sdo/aia'
     data_dir = join(home, 'activeregions/AR11153/data/')
-    maps_dir = join(home, 'activeregions/AR11153/images/')
+    maps_dir = join(home, 'activeregions/AR11153/images/')"""
+    data_dir = '/imaps/sspfs/archive/sdo/aia/activeregions/AR11153/data/'
+    maps_dir = '/imaps/holly/home/ajl7/tempmaps'
     
     for time in times:
         # Load/calculate temperature map data

### 2014-12-11 plotflares3.py
Debugging error message

@@ -67,8 +67,11 @@ for flare in flares:
     
     for time in times:
         # Load/calculate temperature map data
-        thismap = tmap(time, data_dir=data_dir, maps_dir=maps_dir)
-        thismap.save()
+        try:
+            thismap = tmap(time, data_dir=data_dir, maps_dir=maps_dir)
+            thismap.save()
+        except:
+            print "Failed", time
         
         # Crop temperature map to active region
         x, y = wcs.convert_hg_hpc(region['hgc_x'], region['hgc_y'],

### 2014-12-11 paper.tex
Updates to analysis code
Structure changed slightly to fit guidelines
Plotting of temperature change over time added

@@
 \maketitle
+
+%===========================================================================
+\begin{abstract}
+  This is an abstract
+\end{abstract}
 
@@
 \subsection{Active region analysis}
-The method of Paper I was used to investigate the temperatures of flaring active regions betwen AR11138-AR11183. %substitute dates here
+The method of Paper I was used to investigate the temperatures of the active regions associated with flares which occured betwen 2011-02-01 and 2011-04-01.
+% Currently the dates are 2011/02/10 - 2011/02/16, which needs some fixing
 The first part of the investigation tracked active regions as they moved across the solar disk and plotted their temperature distributions in the hour leading up to a flare.
@@
 \section{Results}
-Figures 1 and 2 show the mean, standard deviation, 95th percentile and maximum temperature of active regions AR11146 and AR11149 respectively, as functions of time.
+%Figures 1 and 2 show the mean, standard deviation, 95th percentile and maximum temperature of active regions AR11146 and AR11149 respectively, as functions of time.
+%None of this is true6 becaus6e I'm not doing those plots any more
 The times of the associated flares are also plotted.
@@
 %===========================================================================
-\section{Discussion}
+\section{Discussion and conclusions}
 
@@
 %===========================================================================
-\section{Conclusions}
+\section*{Acknowledgements}
+
+%===========================================================================
+\section*{annexes}
 

### 2014-12-11 plotflares3.py

@@ -7,6 +7,8 @@ Created on Tue Dec 09 18:15:45 2014
 
 from matplotlib import use
 use('agg')
+import numpy as np
+import matplotlib.pyplot as plt
 from sunpy import wcs
 from sunpy.net import hek
 from sunpy.time import parse_time as parse
@@ -35,6 +37,7 @@ datefile.write('')
 datefile.close()
 
 ar_rad = 75
+ar_temps = []
 
 for flare in flares:
     flaretime = parse(flare['event_starttime'])
@@ -65,23 +68,31 @@ for flare in flares:
     data_dir = '/imaps/sspfs/archive/sdo/aia/activeregions/AR11153/data/'
     maps_dir = '/imaps/holly/home/ajl7/tempmaps'
     
+    means = []
     for time in times:
         # Load/calculate temperature map data
         try:
             thismap = tmap(time, data_dir=data_dir, maps_dir=maps_dir)
             thismap.save()
+        
+            # Crop temperature map to active region
+            x, y = wcs.convert_hg_hpc(region['hgc_x'], region['hgc_y'],
+                                      b0_deg=thismap.heliographic_latitude,
+                                      l0_deg=thismap.carrington_longitude)
+            thismap = thismap.submap([x-ar_rad, x+ar_rad], [y-ar_rad, y+ar_rad])
+            
+            # Append appropriate temperature values to list
+            means.append(np.nanmean(thismap.data))
         except:
             print "Failed", time
-        
-        # Crop temperature map to active region
-        x, y = wcs.convert_hg_hpc(region['hgc_x'], region['hgc_y'],
-                                  b0_deg=thismap.heliographic_latitude,
-                                  l0_deg=thismap.carrington_longitude)
-        thismap = thismap.submap([x-ar_rad, x+ar_rad], [y-ar_rad, y+ar_rad])
-        
-        # Append appropriate temperature values to list
+            means.append(np.nan)
     
     # Append  temperature values for final temperature map to list
+    ar_temps.append(means[-1])
+    # Convert time values to time before flare
+    times = [(t - flaretime).total_seconds()/60 for t in times]
     # Plot temperature values of AR with time for that flare
+    fig = plt.figure()
+    plt.plot(times, means)
     
 # Plot instantaneous temperatures of active regions for all flares

### 2014-12-11 plotflares3.py
Now with added figure saving

@@ -94,5 +94,9 @@ for flare in flares:
     # Plot temperature values of AR with time for that flare
     fig = plt.figure()
     plt.plot(times, means)
+    fname = '{}flare_at_{:%Y%m%dT%H%M}'.format(flare['fl_goescls'],
+                                               flare['event_starttime'])
+    plt.savefig(fname)
+    plt.close()
     
 # Plot instantaneous temperatures of active regions for all flares

### 2014-12-12 plotflares3.py
Adjust plot saving

@@ -96,7 +96,7 @@ for flare in flares:
     plt.plot(times, means)
     fname = '{}flare_at_{:%Y%m%dT%H%M}'.format(flare['fl_goescls'],
                                                flare['event_starttime'])
-    plt.savefig(fname)
+    plt.savefig(join('/imaps/holly/home/ajl7/tempplots/', fname))
     plt.close()
     
 # Plot instantaneous temperatures of active regions for all flares

### 2014-12-12 plotflares3.py
Debugging

@@ -40,6 +40,7 @@ ar_rad = 75
 ar_temps = []
 
 for flare in flares:
+  try:
     flaretime = parse(flare['event_starttime'])
     starttime = flaretime-dt.timedelta(hours=0.5)
     timerange = tr(starttime, flaretime)
@@ -94,9 +95,13 @@ for flare in flares:
     # Plot temperature values of AR with time for that flare
     fig = plt.figure()
     plt.plot(times, means)
-    fname = '{}flare_at_{:%Y%m%dT%H%M}'.format(flare['fl_goescls'],
+    print flare['fl_goescls'], flare['event_starttime']
+    fname = '{}flare_at_'.format(flare['fl_goescls'],
                                                flare['event_starttime'])
     plt.savefig(join('/imaps/holly/home/ajl7/tempplots/', fname))
     plt.close()
+  except:
+    print 'Failed for {} flare at {}'.format(flare['fl_goescls'], flare['event_starttime'])
+    raise
     
 # Plot instantaneous temperatures of active regions for all flares

### 2014-12-12 plotflares3.py
Plot save debugging

@@ -96,8 +96,8 @@ for flare in flares:
     fig = plt.figure()
     plt.plot(times, means)
     print flare['fl_goescls'], flare['event_starttime']
-    fname = '{}flare_at_'.format(flare['fl_goescls'],
-                                               flare['event_starttime'])
+    fname = '{}flare_at_'.format(flare['fl_goescls'], flare['event_starttime'])
+    fname.replace('.', '_')
     plt.savefig(join('/imaps/holly/home/ajl7/tempplots/', fname))
     plt.close()
   except:

### 2014-12-12 plotflares3.py
Various debugging and stuff

@@ -19,7 +19,7 @@ from sys import path
 path.append('/imaps/holly/home/ajl7/CoronaTemps/')
 from temperature import TemperatureMap as tmap
 
-start = parse('2011-02-10')
+start = parse('2011-02-01')
 end = parse('2011-04-01')
 
 client = hek.HEKClient()
@@ -95,9 +95,8 @@ for flare in flares:
     # Plot temperature values of AR with time for that flare
     fig = plt.figure()
     plt.plot(times, means)
-    print flare['fl_goescls'], flare['event_starttime']
-    fname = '{}flare_at_'.format(flare['fl_goescls'], flare['event_starttime'])
-    fname.replace('.', '_')
+    fname = '{}__{}-class'.format(flare['event_starttime'], flare['fl_goescls'])
+    fname = fname.replace('.', '_')
     plt.savefig(join('/imaps/holly/home/ajl7/tempplots/', fname))
     plt.close()
   except:

### 2014-12-16 paper.tex
More description of temperature map method added

@@
 
+Although it is faster than others of its kind, the temperature-calculating method used here takes some time to analyse all the required data.
+As such this is a preliminary work and the results should not be considered definitive.
+Rather they are a demonstration of the type of study made available by fast temperature analysis of the corona, which until recently has not been possible.
+
 This method uses SunPy, a free, open-source Python library for solar physics.
@@
 This allows the temperature of the corona to be estimated for every pixel of an AIA image, resulting in very high resolution temperature maps.
+Crucially, this method produces temperature maps extremely quickly, which allows us to investigate coronal temperatures during localised dynamic events such as flares.
+With other, slower methods, such studies are infeasible due to the computation time required.
+An example temperature map is shown in Figure X. % Include an example temperature map
 
@@
 The method of Paper I was used to investigate the temperatures of the active regions associated with flares which occured betwen 2011-02-01 and 2011-04-01.
-% Currently the dates are 2011/02/10 - 2011/02/16, which needs some fixing
-The first part of the investigation tracked active regions as they moved across the solar disk and plotted their temperature distributions in the hour leading up to a flare.
+The specific active regions investigated are listed in Table X along with the flares associated with each.
+% Include a table of the flares looked at, when they occured and which active region they're associated with.
+The first part of the investigation tracked the active regions as they moved across the solar disk and plotted their temperature distributions in the hour leading up to a flare.
 Then the temperatures of the associated active regions were directly compared for each of the investigated flares.
@@
 \section{Discussion and conclusions}
+From this study, it appears that there is no clear link between solar flares and coronal temperatures.
+However, it is worth remembering that
 

### 2014-12-16 paper.tex
Added some discussion to  the discussion

@@
 From this study, it appears that there is no clear link between solar flares and coronal temperatures.
-However, it is worth remembering that
+This is probably mostly due to the relatively small number of flares studied - a much larger sample size would have to be used to properly determine any link or lack thereof.
+However, this work does demonstrate that it is now possible to study temperature distributions of the corona in high resolution and on short timescales using fast temperature analysis tools such as that described in Paper 1.
 

### 2014-12-17 plotflares3.py
More debugging and some tidying

@@ -29,13 +29,6 @@ flares = client.query(hek.attrs.Time(start, end),
 flares = [fl for fl in flares if (fl['ar_noaanum'] > 11137 and 
                                   fl['ar_noaanum'] < 11184)]
 
-fluxes = []
-temps = []
-coords = []
-datefile = open('dates.txt', 'w')
-datefile.write('')
-datefile.close()
-
 ar_rad = 75
 ar_temps = []
 
@@ -55,7 +48,8 @@ for flare in flares:
     if isinstance(region, list):
         try:
             region = region[0]
-        except IndexError:
+        except:# IndexError:
+            print "An error occured for active region AR{}".format(flare['ar_noaanum'])
             continue
     
     # Define times for maps
@@ -66,7 +60,7 @@ for flare in flares:
     """home = '/imaps/sspfs/archive/sdo/aia'
     data_dir = join(home, 'activeregions/AR11153/data/')
     maps_dir = join(home, 'activeregions/AR11153/images/')"""
-    data_dir = '/imaps/sspfs/archive/sdo/aia/activeregions/AR11153/data/'
+    data_dir = '/imaps/sspfs/archive/sdo/aia/activeregions/AR{}/data/'.format(flare['ar_noaanum'])
     maps_dir = '/imaps/holly/home/ajl7/tempmaps'
     
     means = []
@@ -87,6 +81,7 @@ for flare in flares:
         except:
             print "Failed", time
             means.append(np.nan)
+            raise
     
     # Append  temperature values for final temperature map to list
     ar_temps.append(means[-1])
@@ -95,12 +90,12 @@ for flare in flares:
     # Plot temperature values of AR with time for that flare
     fig = plt.figure()
     plt.plot(times, means)
-    fname = '{}__{}-class'.format(flare['event_starttime'], flare['fl_goescls'])
+    fname = 'AR{}/{}__{}-class'.format(flare['ar_noaanum'], flare['event_starttime'], flare['fl_goescls'])
     fname = fname.replace('.', '_')
     plt.savefig(join('/imaps/holly/home/ajl7/tempplots/', fname))
     plt.close()
   except:
     print 'Failed for {} flare at {}'.format(flare['fl_goescls'], flare['event_starttime'])
-    raise
+    #raise
     
 # Plot instantaneous temperatures of active regions for all flares

### 2015-01-19 paper.tex
Minor additions

@@
 % Include a table of the flares looked at, when they occured and which active region they're associated with.
-The first part of the investigation tracked the active regions as they moved across the solar disk and plotted their temperature distributions in the hour leading up to a flare.
+
+\begin{table}
+	\centering
+		\begin{tabular}
+
+		\end{tabular}
+	\caption{Times and associated active regions of solar flares studied}
+	\label{tab:flares}
+	% Many of these won't be there because of not working
+\end{table}
+
+The first part of the investigation tracked the active regions as they moved across the solar disk and plotted their temperature distributions in the 30 minutes leading up to a flare.
 Then the temperatures of the associated active regions were directly compared for each of the investigated flares.
+
+Sample temperature maps demonstrating the tracking of the active regions are shown in Figures Y - Z
 
@@
 For each flare event investigated, a temperature map was calculated for a 50x50 arcsec area around the corresponding active region at 1-minute intervals for the hour preceding the event.
+% 150x150 arcsec I think?
+change this
 The times of the flares and the locations of the active regions on the solar disk were obtained by querying the Heliophysics Events Knowledgebase (HEK).
 How the temperature distribution changes with time was then compared to when associated flares occur for each active region.
-The mean (and standard deviation? percentiles?) of the temperature map was calculated at each time step and these values were plotted for each flare.
+The mean (and standard deviation? percentiles?, etc) of the temperature map was calculated at each time step and these values were plotted for each flare.
 

### 2015-01-19 plotflares3.py
Various plotting additions

@@ -57,7 +57,7 @@ def flareclass_to_flux(flareclass):
 
 
 start = parse('2011-02-01')
-end = parse('2011-04-01')
+end = parse('2011-03-01')
 
 client = hek.HEKClient()
 flares = client.query(hek.attrs.Time(start, end),
@@ -67,8 +67,15 @@ flares = [fl for fl in flares if (fl['ar_noaanum'] > 11137 and
                                   fl['ar_noaanum'] < 11184)]
 
 ar_rad = 75
-ar_temps = []
+ar_temps_fltime = []
+ar_temps_1 = []
+ar_temps_10 = []
+ar_temps_30 = []
 fl_classes = []
+
+flarelist = open("flarelist.txt", w)
+
+fig = plt.figure()
 
 for flare in flares:
   try:
@@ -76,6 +83,7 @@ for flare in flares:
     starttime = flaretime-dt.timedelta(hours=0.5)
     timerange = tr(starttime, flaretime)
 
+    flarelist.write(flaretime.date, flaretime.time, "&", flare['fl_goescls'], "&", flare['ar_noaanum'], "\\\\")
     region = client.query(hek.attrs.EventType('AR'),
                           hek.attrs.Time(flaretime-dt.timedelta(minutes=5), 
                                          flaretime))
@@ -99,14 +107,16 @@ for flare in flares:
     data_dir = join(home, 'activeregions/AR11153/data/')
     maps_dir = join(home, 'activeregions/AR11153/images/')"""
     data_dir = '/imaps/sspfs/archive/sdo/aia/activeregions/AR{}/data/'.format(flare['ar_noaanum'])
-    maps_dir = '/imaps/holly/home/ajl7/tempmaps'
+    maps_root = '/imaps/sspfs/archive/sdo/aia/fulldisk/images/' #'/imaps/holly/home/ajl7/tempmaps'
     
     means = []
     for time in times:
         # Load/calculate temperature map data
+        print time
         try:
+            maps_dir = join(maps_root, "{:%Y/%m/%d}/temperature/".format(time))
             thismap = tmap(time, data_dir=data_dir, maps_dir=maps_dir)
-            thismap.save()
+            #thismap.save()
         
             # Crop temperature map to active region
             x, y = wcs.convert_hg_hpc(region['hgc_x'], region['hgc_y'],
@@ -119,27 +129,51 @@ for flare in flares:
         except:
             print "Failed", time
[…]

### 2015-01-21 plotflares3.py
More various plotting things added

@@ -9,6 +9,8 @@ from matplotlib import use
 use('agg')
 import numpy as np
 import matplotlib.pyplot as plt
+import matplotlib.cm as cmx
+import matplotlib.colors as colours
 from sunpy import wcs
 from sunpy.net import hek
 from sunpy.time import parse_time as parse
@@ -73,9 +75,20 @@ ar_temps_10 = []
 ar_temps_30 = []
 fl_classes = []
 
-flarelist = open("flarelist.txt", w)
+flarelist = open("/imaps/holly/home/ajl7/tempplots/flarelist.txt", "w")
 
-fig = plt.figure()
+fig = plt.figure(figsize=(24, 8))
+ax1 = fig.add_subplot(1, 3, 1)
+ax1.set_title('Temperature value over time')
+ax2 = fig.add_subplot(1, 3, 2)
+ax2.set_title('Running difference')
+ax3 = fig.add_subplot(1, 3, 3)
+ax3.set_title('Difference from temperature at flare time')
+
+# Set up some colourmap stuff for line-plotting later
+cmap = cm = plt.get_cmap('afmhot')
+cNorm  = colours.Normalize(vmin=0, vmax=1)
+scalarMap = cmx.ScalarMappable(norm=cNorm, cmap=cmap)
 
 for flare in flares:
   try:
@@ -83,7 +96,7 @@ for flare in flares:
     starttime = flaretime-dt.timedelta(hours=0.5)
     timerange = tr(starttime, flaretime)
 
-    flarelist.write(flaretime.date, flaretime.time, "&", flare['fl_goescls'], "&", flare['ar_noaanum'], "\\\\")
+    flarelist.write("{} {} & {} & {} \\\\ \n".format(flaretime.date(), flaretime.time(), flare['fl_goescls'], flare['ar_noaanum']))
     region = client.query(hek.attrs.EventType('AR'),
                           hek.attrs.Time(flaretime-dt.timedelta(minutes=5), 
                                          flaretime))
@@ -109,7 +122,11 @@ for flare in flares:
     data_dir = '/imaps/sspfs/archive/sdo/aia/activeregions/AR{}/data/'.format(flare['ar_noaanum'])
     maps_root = '/imaps/sspfs/archive/sdo/aia/fulldisk/images/' #'/imaps/holly/home/ajl7/tempmaps'
     
+    # Create empty lists to store temperature values and running differences
[…]

### 2015-01-26 plotflares3.py
More plotting stuff added and amended

@@ -17,6 +17,7 @@ from sunpy.time import parse_time as parse
 from sunpy.time.timerange import TimeRange as tr
 import datetime as dt
 from os.path import join
+import sys
 from sys import path
 path.append('/imaps/holly/home/ajl7/CoronaTemps/')
 from temperature import TemperatureMap as tmap
@@ -77,13 +78,27 @@ fl_classes = []
 
 flarelist = open("/imaps/holly/home/ajl7/tempplots/flarelist.txt", "w")
 
-fig = plt.figure(figsize=(24, 8))
-ax1 = fig.add_subplot(1, 3, 1)
-ax1.set_title('Temperature value over time')
-ax2 = fig.add_subplot(1, 3, 2)
-ax2.set_title('Running difference')
-ax3 = fig.add_subplot(1, 3, 3)
-ax3.set_title('Difference from temperature at flare time')
+absfig = plt.figure(figsize=(24, 8))
+axs1 = absfig.add_subplot(1, 3, 1)
+axs1.set_title('Temperature value over time')
+axs2 = absfig.add_subplot(1, 3, 2)
+axs2.set_title('Running difference')
+axs3 = absfig.add_subplot(1, 3, 3)
+axs3.set_title('Difference from temperature at flare time')
+
+ratfig = plt.figure(figsize=(10, 10))
+axr1 = ratfig.add_subplot(2, 2, 1)
+axr1.set_title("T(t)/T(t=x)")
+axr1.set_ylabel("Temperature ratio")
+axr2 = ratfig.add_subplot(2, 2, 2)
+axr2.set_title("T(t)/T(t=-1)")
+axr3 = ratfig.add_subplot(2, 2, 3)
+axr3.set_title("T(t)/T(t=-10)")
+axr3.set_ylabel("Temperature ratio")
+axr3.set_xlabel("Time (minutes)")
+axr4 = ratfig.add_subplot(2, 2, 4)
+axr4.set_title("T(t)/T(t=-30)")
+axr4.set_xlabel("Time (minutes)")
 
 # Set up some colourmap stuff for line-plotting later
 cmap = cm = plt.get_cmap('afmhot')
@@ -96,7 +111,6 @@ for flare in flares:
     starttime = flaretime-dt.timedelta(hours=0.5)
     timerange = tr(starttime, flaretime)
 
[…]

### 2015-01-26 plotflares3.py
Brain-fart removal

@@ -79,12 +79,12 @@ fl_classes = []
 flarelist = open("/imaps/holly/home/ajl7/tempplots/flarelist.txt", "w")
 
 absfig = plt.figure(figsize=(24, 8))
-axs1 = absfig.add_subplot(1, 3, 1)
-axs1.set_title('Temperature value over time')
-axs2 = absfig.add_subplot(1, 3, 2)
-axs2.set_title('Running difference')
-axs3 = absfig.add_subplot(1, 3, 3)
-axs3.set_title('Difference from temperature at flare time')
+axa1 = absfig.add_subplot(1, 3, 1)
+axa1.set_title('Temperature value over time')
+axa2 = absfig.add_subplot(1, 3, 2)
+axa2.set_title('Running difference')
+axa3 = absfig.add_subplot(1, 3, 3)
+axa3.set_title('Difference from temperature at flare time')
 
 ratfig = plt.figure(figsize=(10, 10))
 axr1 = ratfig.add_subplot(2, 2, 1)

### 2015-01-27 plotARs.py
Plotting code added for demonstrating AR tracking

@@ -1,0 +1,59 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jan 26 15:41:43 2015
+
+@author: Drew Leonard
+"""
+
+from matplotlib import use
+use('agg')
+from sunpy import wcs
+from sunpy.net import hek
+from sunpy.time import parse_time as parse
+from sunpy.time.timerange import TimeRange as tr
+import datetime as dt
+from sys import path
+path.append('/home/drew/CoronaTemps/')
+from temperature import TemperatureMap as tmap
+
+
+start = parse('2011-02-15 01:45')
+end = parse('2011-02-16 02:15')
+
+client = hek.HEKClient()
+flares = client.query(hek.attrs.Time(start, end),
+                      hek.attrs.EventType('FL'))
+
+flare = [fl for fl in flares if (fl['ar_noaanum'] == 11158)][0]
+
+ar_rad = 75
+
+flaretime = parse(flare['event_starttime'])
+starttime = flaretime-dt.timedelta(hours=0.5)
+timerange = tr(starttime, flaretime)
+
+region = client.query(hek.attrs.EventType('AR'),
+                      hek.attrs.Time(flaretime-dt.timedelta(minutes=5), 
+                                     flaretime))
+if isinstance(region, list): region = region[0]
+
+# Define times for maps
+delta = dt.timedelta(minutes=10)
+ntimes = int(timerange.seconds()/delta.total_seconds())
+times = [time.start() for time in timerange.split(ntimes)]
+
+for time in times:
+    # Load/calculate temperature map data
+    print time
+    #maps_dir = join(maps_root, "{:%Y/%m/%d}/temperature/".format(time))
+    thismap = tmap(time)#, data_dir=data_dir, maps_dir=maps_dir)
+    thismap.save()
+
+    # Crop temperature map to active region
+    x, y = wcs.convert_hg_hpc(region['hgc_x'], region['hgc_y'],
+                              b0_deg=thismap.heliographic_latitude,
+                              l0_deg=thismap.carrington_longitude)
+    thismap = thismap.submap([x-ar_rad, x+ar_rad], [y-ar_rad, y+ar_rad])
+    
+    # Plot temperature map with it's 171A counterpart and a context image
+    thismap.compare('171')

### 2015-01-27 paper.tex
Massive table of flares added
Tracking description added

@@
 
+The Paper I method also allows easy 'tracking' of solar regions by cropping the temperature map around a set of Carrington heliographic coordinates, which rotate at approximately the rate of solar rotation.
+This tracking is demonstrated in Figures A, B and C, each of which shows a cropped region of an AIA 17.1nm image containing active region AR11185, the corresponding temperature map and a larger 17.1nm image showing the location of the region in the corona.
+
 \subsection{Active region analysis}
@@
 	\centering
-		\begin{tabular}
+		\begin{tabular}{c|c|c}
+			Date and time & GOES class & NOAA Active region \\
+			\hline
 

### 2015-01-28 plotflares3.py
Significant plotting changes and additions

@@ -76,17 +76,21 @@ ar_temps_10 = []
 ar_temps_30 = []
 fl_classes = []
 
-flarelist = open("/imaps/holly/home/ajl7/tempplots/flarelist.txt", "w")
+flarelist = open("/imaps/holly/home/ajl7/tempplots_max/flarelist.txt", "w")
 
-absfig = plt.figure(figsize=(24, 8))
-axa1 = absfig.add_subplot(1, 3, 1)
-axa1.set_title('Temperature value over time')
-axa2 = absfig.add_subplot(1, 3, 2)
-axa2.set_title('Running difference')
-axa3 = absfig.add_subplot(1, 3, 3)
-axa3.set_title('Difference from temperature at flare time')
+absfig, (axa1, axa2, axa3) = plt.subplots(3, 2, sharex='col', sharey='row', figsize=(16, 24))
+axa1[0].set_title('A, B and C class flares')
+axa1[1].set_title('M and X class flares')
+axa1[0].set_ylabel('Max log(T)')
+axa2[0].set_ylabel('Running difference max log(T)')
+axa3[0].set_ylabel('log(T) difference from flare onset time')
+axa3[0].set_xlabel('Time (minutes before flare onset)')
+axa3[1].set_xlabel('Time (minutes before flare onset)')
+limits1 = (1000, -1000)
+limits2 = (1000, -1000)
+limits3 = (1000, -1000)
 
-ratfig = plt.figure(figsize=(10, 10))
+"""ratfig = plt.figure(figsize=(10, 10))
 axr1 = ratfig.add_subplot(2, 2, 1)
 axr1.set_title("T(t)/T(t=x)")
 axr1.set_ylabel("Temperature ratio")
@@ -98,7 +102,7 @@ axr3.set_ylabel("Temperature ratio")
 axr3.set_xlabel("Time (minutes)")
 axr4 = ratfig.add_subplot(2, 2, 4)
 axr4.set_title("T(t)/T(t=-30)")
-axr4.set_xlabel("Time (minutes)")
+axr4.set_xlabel("Time (minutes)")"""
 
 # Set up some colourmap stuff for line-plotting later
 cmap = cm = plt.get_cmap('afmhot')
@@ -167,33 +171,38 @@ for flare in flares:
         except:
             failed = True
             print "Failed", time
-            means.append(np.nan)
-            #raise
+            #means.append(np.nan)
+            raise
 
     #print means
[…]

### 2015-01-28 plotflares3.py
Plotting tweaks and automatic r6enaming of things added

@@ -59,8 +59,11 @@ def flareclass_to_flux(flareclass):
     return flux
 
 
+parameter = 'max'
+savedir = "/imaps/holly/home/ajl7/tempplots_{}/".format(parameter)
+
 start = parse('2011-02-01')
-end = parse('2011-03-01')
+end = parse('2011-02-02')
 
 client = hek.HEKClient()
 flares = client.query(hek.attrs.Time(start, end),
@@ -76,13 +79,13 @@ ar_temps_10 = []
 ar_temps_30 = []
 fl_classes = []
 
-flarelist = open("/imaps/holly/home/ajl7/tempplots_max/flarelist.txt", "w")
+flarelist = open(join(savedir, "flarelist.txt"), "w")
 
 absfig, (axa1, axa2, axa3) = plt.subplots(3, 2, sharex='col', sharey='row', figsize=(16, 24))
 axa1[0].set_title('A, B and C class flares')
 axa1[1].set_title('M and X class flares')
-axa1[0].set_ylabel('Max log(T)')
-axa2[0].set_ylabel('Running difference max log(T)')
+axa1[0].set_ylabel('{} log(T)'.format(parameter.title()))
+axa2[0].set_ylabel('Running difference {} log(T)'.format(parameter))
 axa3[0].set_ylabel('log(T) difference from flare onset time')
 axa3[0].set_xlabel('Time (minutes before flare onset)')
 axa3[1].set_xlabel('Time (minutes before flare onset)')
@@ -134,9 +137,6 @@ for flare in flares:
     ntimes = int(timerange.seconds()/delta.total_seconds())
     times = [time.start() for time in timerange.split(ntimes)]
     
-    """home = '/imaps/sspfs/archive/sdo/aia'
-    data_dir = join(home, 'activeregions/AR11153/data/')
-    maps_dir = join(home, 'activeregions/AR11153/images/')"""
     data_dir = '/imaps/sspfs/archive/sdo/aia/activeregions/AR{}/data/'.format(flare['ar_noaanum'])
     maps_root = '/imaps/sspfs/archive/sdo/aia/fulldisk/images/' #'/imaps/holly/home/ajl7/tempmaps'
     
@@ -225,8 +225,8 @@ flarelist.close()
 axa1[0].set_ylim(limits1[0]-0.02, limits1[1]+0.02)
 axa2[0].set_ylim(limits2[0]-0.005, limits2[1]+0.005)
[…]

### 2015-01-28 plotflares3.py
automatic function changing

@@ -59,7 +59,16 @@ def flareclass_to_flux(flareclass):
     return flux
 
 
-parameter = 'max'
+def p95(data):
+    return np.percentile(data, 95)
+
+
+def p5(data):
+    return np.percentile(data, 5)
+
+
+parameter = 'mean'
+functions = {'mean': np.nanmean, 'max': np.nanmax, 'p95': p95, 'p5': p5}
 savedir = "/imaps/holly/home/ajl7/tempplots_{}/".format(parameter)
 
 start = parse('2011-02-01')
@@ -160,9 +169,7 @@ for flare in flares:
             thismap = thismap.submap([x-ar_rad, x+ar_rad], [y-ar_rad, y+ar_rad])
 
             # Append appropriate temperature values to list
-            #means.append(np.nanmean(thismap.data))
-            means.append(np.nanmax(thismap.data))
-            #means.append(np.percentile(thismap.data, 95))
+            means.append(functions[parameter](thismap.data))
             if len(means) > 1:
                 runningdiffT.append(means[-1]-means[-2])
             else:

### 2015-01-29 plotARs.py
Tracking demo images added

@@ -26,34 +26,36 @@ flares = client.query(hek.attrs.Time(start, end),
 
 flare = [fl for fl in flares if (fl['ar_noaanum'] == 11158)][0]
 
-ar_rad = 75
-
 flaretime = parse(flare['event_starttime'])
-starttime = flaretime-dt.timedelta(hours=0.5)
+starttime = flaretime-dt.timedelta(hours=6)
 timerange = tr(starttime, flaretime)
 
 region = client.query(hek.attrs.EventType('AR'),
                       hek.attrs.Time(flaretime-dt.timedelta(minutes=5), 
-                                     flaretime))
-if isinstance(region, list): region = region[0]
+                                     flaretime),
+                      hek.attrs.AR.NOAANum == 11158)
+
+if isinstance(region, list): region = region[1]
+
+print region['ar_noaanum']
 
 # Define times for maps
-delta = dt.timedelta(minutes=10)
+delta = dt.timedelta(hours=2)
 ntimes = int(timerange.seconds()/delta.total_seconds())
 times = [time.start() for time in timerange.split(ntimes)]
 
 for time in times:
     # Load/calculate temperature map data
-    print time
-    #maps_dir = join(maps_root, "{:%Y/%m/%d}/temperature/".format(time))
-    thismap = tmap(time)#, data_dir=data_dir, maps_dir=maps_dir)
+    thismap = tmap(time)
     thismap.save()
 
     # Crop temperature map to active region
     x, y = wcs.convert_hg_hpc(region['hgc_x'], region['hgc_y'],
                               b0_deg=thismap.heliographic_latitude,
                               l0_deg=thismap.carrington_longitude)
-    thismap = thismap.submap([x-ar_rad, x+ar_rad], [y-ar_rad, y+ar_rad])
+    #thismap = thismap.submap([x-ar_rad, x+ar_rad], [y-ar_rad, y+ar_rad])
+    thismap = thismap.region_map(region, mapradius=75)
     
     # Plot temperature map with it's 171A counterpart and a context image
-    thismap.compare('171')
+    thismap.compare('171', context_wlen='171', 
+                    savedir='/home/drew/statistical_challenges_in_SIP/')

### 2015-01-29 plotflares3.py

@@ -188,10 +188,10 @@ for flare in flares:
     ##plt.close()
 
     # Plot ratio of temperatures to given temperature over time
-    axr1.plot(times, [mean/means[-1] for mean in means], label='x = 0', color=ColourVal)
-    axr2.plot(times, [mean/means[-2] for mean in means], label='x = -1', color=ColourVal)
-    axr3.plot(times, [mean/means[-11] for mean in means], label='x = -10', color=ColourVal)
-    axr4.plot(times, [mean/means[0] for mean in means], label='x = -30', color=ColourVal)
+    axr1.plot(times, [mean/means[-1] for mean in means], label='x = 0', color=colourVal)
+    axr2.plot(times, [mean/means[-2] for mean in means], label='x = -1', color=colourVal)
+    axr3.plot(times, [mean/means[-11] for mean in means], label='x = -10', color=colourVal)
+    axr4.plot(times, [mean/means[0] for mean in means], label='x = -30', color=colourVal)
     #plt.ylim(0, 1)
     #plt.legend()
 

### 2015-01-30 paper.tex
Images added to paper and tidying up

@@
-\documentclass{article}
+\documentclass[referee,a4paper,12pt,traditabstract]{swsc}
 
-\author{Andrew Leonard and Huw Morgan}
-%\email{ajl7@aber.ac.uk}
-%\institution{Institute of Mathematics, Physics and Computer Science, Aberystwyth University, Ceredigion, SY23 3BZ, Wales}
+\usepackage{graphicx}
+\usepackage{txfonts}
+\usepackage{subfigure}
+\usepackage{epstopdf}
+\usepackage{lineno}
+\usepackage[authoryear,round]{natbib}
+\usepackage[backref]{hyperref}
+\usepackage{url}
 
-%\author{Huw Morgan}
-%\email{hum2@aber.ac.uk}
-%\institution{Institute of Mathematics, Physics and Computer Science, Aberystwyth University, Ceredigion, SY23 3BZ, Wales}
+\author{A. Leonard \and H. Morgan}
+
+\institute{Institute of Mathematics, Physics and Computer Science, Aberystwyth University, Ceredigion, SY23 3BZ, Wales\\
+					 \email{ajl7@aber.ac.uk}}
 
@@
 
+\begin{linenumbers}
+
+\titlerunning{Temperature distributions of active regions}
+\authorrunning{Leonard and Morgan}
+\abstract{This is an abstract}
+\keywords{}
+
 \maketitle
-
-%===========================================================================
-\begin{abstract}
-  This is an abstract
-\end{abstract}
 
@@
 With other, slower methods, such studies are infeasible due to the computation time required.
-An example temperature map is shown in Figure X. % Include an example temperature map
+An example temperature map is shown in Figure X.
 
 The Paper I method also allows easy 'tracking' of solar regions by cropping the temperature map around a set of Carrington heliographic coordinates, which rotate at approximately the rate of solar rotation.
-This tracking is demonstrated in Figures A, B and C, each of which shows a cropped region of an AIA 17.1nm image containing active region AR11185, the corresponding temperature map and a larger 17.1nm image showing the location of the region in the corona.
+This tracking is demonstrated in Figures \ref{fig:trackdemo1} and \ref{fig:trackdemo2}, each of which shows a cropped region of an AIA 17.1nm image containing active region AR11158, the corresponding temperature map and a larger 17.1nm image showing the location of the region in the corona.
+
+\begin{figure}
+	\centering
+		\includegraphics[scale=0.25]{20110214T194400with171.png}
+	\caption{Top left: Cropped 17.1nm AIA image showing active region AR 11158 at 2011-02-14 19:44:00.
+Top right: temperature map of active region AR11158 at 2011-02-14 19:44:00.
+Bottom: Larger 17.1nm image; the blue square outlines the region shown in the top images.}
+	\label{fig:trackdemo1}
+\end{figure}
+\begin{figure}
+	\centering
+		\includegraphics[scale=0.25]{20110214T234400with171.png}
+	\caption{The same images as Figure \ref{fig:trackdemo1} for time 2011-02-14 23:44:00}
+	\label{fig:trackdemo2}
+\end{figure}
 
@@
 Then the temperatures of the associated active regions were directly compared for each of the investigated flares.
-
-Sample temperature maps demonstrating the tracking of the active regions are shown in Figures Y - Z
 
@@
 
-\subsubsection{Long-term temperature distribution}
+\subsection{Long-term temperature distribution}
 Figures 1 and 2 show that there is no clear trend in the long-term temperature distribution before flares occur.
@@
 
-\subsubsection{Temperatures of active regions before flares}
+\subsection{Temperatures of active regions before flares}
 From figure 3 it can be seen that there does appear to be some grouping of flaring active regions into groups of temperatures, and that a few of the larger flares are associated with active regions at higher temperatures than most of the other flares investigated.
@@
 
+\end{linenumbers}
 \end{document}

### 2015-01-30 paper.tex
Some figures added/amended and some writing added

@@
 \subsection{Temperature analysis}
-The core of this analysis is the temperature map method described by \cite{Leonard2014} (henceforth Paper I).
+The core of this analysis is the temperature map method described by \cite{Leonard} (henceforth Paper I).
 Briefly, this method compares the relative brightnesses in each AIA wavelength channel at a given time and infers the best-fitting temperature from that comparison.
@@
 With other, slower methods, such studies are infeasible due to the computation time required.
-An example temperature map is shown in Figure X.
+An example temperature map is shown in Figure \ref{fig:example_tmap}.
 
@@
 	\centering
-		\includegraphics[scale=0.25]{20110214T194400with171.png}
+		\includegraphics[width=\columnwidth]{2011-02-15T00_00_00.png}
+	\caption{Example temperature map for the full solar corona at 2011-02-15 00:00}
+	\label{fig:example_tmap}
+\end{figure}
+
+\begin{figure}
+	\centering
+		\includegraphics[width=0.9\columnwidth]{20110214T194400with171.png}
 	\caption{Top left: Cropped 17.1nm AIA image showing active region AR 11158 at 2011-02-14 19:44:00.
@@
 	\centering
-		\includegraphics[scale=0.25]{20110214T234400with171.png}
-	\caption{The same images as Figure \ref{fig:trackdemo1} for time 2011-02-14 23:44:00}
+		\includegraphics[width=0.9\columnwidth]{20110214T234400with171.png}
+	\caption{The same images as Figure \ref{fig:trackdemo1} for time 2011-02-14 23:44:00.}
 	\label{fig:trackdemo2}
@@
 \subsection{Active region analysis}
-The method of Paper I was used to investigate the temperatures of the active regions associated with flares which occured betwen 2011-02-01 and 2011-04-01.
-The specific active regions investigated are listed in Table X along with the flares associated with each.
-% Include a table of the flares looked at, when they occured and which active region they're associated with.
+The temperature map method described in Paper I was used to investigate the temperatures of the active regions associated with flares which occured during February 2011.
+This month was chosen because several flares occured during this time with a wide range of peak fluxes.
+The flares detected included many small flares (A, B and C class) as well as several larger M class flares and a single X class flare. % Double-check if there are any A or more Xes
+
+For each flare event investigated, a temperature map was calculated for a 150 x 150 arcsec area around the corresponding active region at 1-minute intervals for the 30 minutes preceding the start of the flare.
+The maximum, 95th percentile, mean, 5th percentile and minimum were then calculated for each temperature map for each flare in order to compare if and how the bulk temperature of the active regions changed before the flare.
+The 95th and 5th percentiles were calculated because the maximum and minimum may be affected by small numbers of unusually high or low temperature pixels, which may not accurately represent how the bulk temperature of the active region changes with time.
+
+The start times of the flares and the locations of the active regions on the solar disk were obtained by querying the Heliophysics Events Knowledgebase (HEK).
+The specific flares investigated are listed in Table \ref{tab:flares} along with the active region associated with each.
+Note that not all flares occuring in this time were studied, since for some flares the neccessary AIA data were not available to temperature map the full 30-minute range before the flare onset.
+Flares with missing data were therefore not studied.
 
@@
 			\hline
-
+			% PUT THINGS HERE
 		\end{tabular}
-	\caption{Times and associated active regions of solar flares studied}
+	\caption{Start times and associated active regions of solar flares studied during 2011-02.}
 	\label{tab:flares}
-	% Many of these won't be there because of not working
 \end{table}
@@
 
-\subsubsection{Long-term temperature distribution}
-For each flare event investigated, a temperature map was calculated for a 50x50 arcsec area around the corresponding active region at 1-minute intervals for the hour preceding the event.
-% 150x150 arcsec I think?
-change this
-The times of the flares and the locations of the active regions on the solar disk were obtained by querying the Heliophysics Events Knowledgebase (HEK).
-How the temperature distribution changes with time was then compared to when associated flares occur for each active region.
-The mean (and standard deviation? percentiles?, etc) of the temperature map was calculated at each time step and these values were plotted for each flare.
-
-\subsubsection{Temperatures of active regions before flares}
-For each flare the 95th percentile temperature was calculated from one temperature map of the corresponding active region.
-This map was chosen as the latest map before the start time of the flare. % was it?
-All flares were then plotted on a scatter graph of this temperature against the peak GOES flux of the flare.
-
 %===========================================================================
 \section{Results}
-%Figures 1 and 2 show the mean, standard deviation, 95th percentile and maximum temperature of active regions AR11146 and AR11149 respectively, as functions of time.
-%None of this is true6 becaus6e I'm not doing those plots any more
-The times of the associated flares are also plotted.
-These regions were chosen as they are typical of the results found for other active regions, and show similar temperature profiles but different numbers of flares.
-In both plots, some time before a flare or group of flares occur, the maximum temperature rises significantly but the bulk temperature of the region varies relatively little.
-Figure 3 plots the peak flux for all flares associated with the studied active regions against the 95th percentile temperature for the corresponding active regions before the beginning of the flare.
-Most of these flares are grouped around log(T) $\approx$ 6.35, 6.55 and 6.7, with fewer flares associated with hotter active regions, generally.
-However, the strongest flares observed do appear to be associated with hotter active regions.
+\subsection{Temperature change over time}
+Figures \ref{fig:allars_max}, \ref{fig:allars_p95}, \ref{fig:allars_mean}, \ref{fig:allars_p5} and \ref{fig:allars_min} show how the temperature properties of the active region changed during the 30 minutes preceding each flare.
+All of the flares studied are plotted in each of these figures so that any changes common to many flares can be easily noticed.
+The maximum, 95th percentile, mean, 5th percentile and minimum are plotted in figures \ref{fig:allars_max}, \ref{fig:allars_p95}, \ref{fig:allars_mean}, \ref{fig:allars_p5} and \ref{fig:allars_min} respectively.
+In each figure, the top panels show the variation of the relevant parameter's value with time, the middle panels show the running difference and the bottom panes show the difference from the value at the start time of the flare.
+A, B and C class flares are plotted in the panels on the left, while M and X class flares are shown on the right. % Again, double-check if there are any A class or multiple X classes
+
+% Description of plots for maximum
+From the plots in Figure \ref{fig:allars_max} it can be seen that the maximum temperature of each active region varies significantly, with no clear increase or decrease at any particular time before the flare.
+This is the case for both small and large flares.
+However, it is perhaps interesting to note that many of the active regions associated with C class flares show temperature spikes which reach much higher temperatures than other ARs studied, even those associated with larger flares.
+
+% Description of plots for 95
+% Description of plots for mean
+% Description of plots for 5
+% Description of plots for minimum
+
+\begin{figure}
+	\centering
+		\includegraphics[width=0.7\columnwidth]{tempplotsmax/allars.png}
+	\caption{Change in maximum temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
+Top: maximum temperature against time.
+Middle: running difference of maximum temperature.
+Bottom: difference of maximum temperature from maximum temperature at flare start time.
+Left: A, B and C class flares, denoted by dark red, orange and yellow lines, respectively.
+Right: M and X class flares, denoted by red and orange lines, repectively.}
+	\label{fig:allars_max}
+\end{figure}
+\begin{figure}
+	\centering
+		\includegraphics[width=0.7\columnwidth]{tempplotsmax/allars.png}
+	\caption{Change in 95th percentile temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
+Plots and colour-coding are the same as in Figure \ref{fig:allars_max}}
+	\label{fig:allars_p95}
+\end{figure}
+\begin{figure}
+	\centering
+		\includegraphics[width=0.7\columnwidth]{tempplotsmean/allars.png}
+	\caption{Change in mean temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
+Plots and colour-coding are the same as in Figure \ref{fig:allars_max}}
+	\label{fig:allars_mean}
+\end{figure}
+\begin{figure}
+	\centering
+		\includegraphics[width=0.7\columnwidth]{tempplotsmax/allars.png}
+	\caption{Change in 5th percentile temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
+Plots and colour-coding are the same as in Figure \ref{fig:allars_max}}
+	\label{fig:allars_p5}
+\end{figure}
+\begin{figure}
+	\centering
+		\includegraphics[width=0.7\columnwidth]{tempplotsmax/allars.png}
+	\caption{Change in minimum temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
+Plots and colour-coding are the same as in Figure \ref{fig:allars_max}}
+	\label{fig:allars_min}
+\end{figure}
+
+\subsection{Flare flux vs temperature}
+For each temperature parameter, the value for each flare was plotted on a scatter graph against the peak flux of the flare (Figures V - Z).
+This was done for four times in each case: 30 minutes before the flare start time, 10 minutes before, 1 minute before and at the flare start time.
+
+% Description of plots for maximum
+Figure \ref{fig:allflares_max} shows that the maximum temperatures of the ARs studied are closely grouped around a few temperature values.
+This remains the case throughout the 30 minutes before the flare, despite the fact that the temperature of many of these active regions rises and falls significantly during this time.
+This sudden increase or decrease of temperature is particularly noticeable in the active regions associated with C class flares, as can also be seen in Figure \ref{fig:allars_max}.
+
+% Description of plots for 95
+% Description of plots for mean
+% Description of plots for 5
+% Description of plots for minimum
+
+\begin{figure}
+	\centering
+		\includegraphics[width=0.9\columnwidth]{tempplotsmax/allflares.png}
+	\caption{Scatter graph of flare peak flux against active region maximum temperature for four different times.
+Top left: 30 minutes before flare start time.
+Top right: 10 minutes before flare start time.
+Bottom left: 1 minute before flare start time.
+Bottom right: flare start time.
+The red and blue arrows indicate the amount by which the temperature of each active region rose or fell respectively since the time of the previous plot.
+In each plot the dashed lines indicate the lower thresholds for A, B, C, M and X class flares.}
+	\label{fig:allflares_max}
+\end{figure}
+\begin{figure}
+	\centering
+		\includegraphics[width=0.9\columnwidth]{tempplotsmax/allflares.png}
+	\caption{Scatter graph of flare peak flux against 95th percentile temperature of the corresponding active regions for the same four times as in Figure \ref{fig:allflares_max}.}
+	\label{fig:allflares_p95}
+\end{figure}
+\begin{figure}
+	\centering
+		\includegraphics[width=0.9\columnwidth]{tempplotsmean/allflares.png}
+	\caption{Scatter graph of flare peak flux against mean temperature of the corresponding active regions for the same four times as in Figure \ref{fig:allflares_max}.}
+	\label{fig:allflares_mean}
+\end{figure}
+\begin{figure}
+	\centering
+		\includegraphics[width=0.9\columnwidth]{tempplotsmax/allflares.png}
+	\caption{Scatter graph of flare peak flux against 95th percentile temperature of the corresponding active regions for the same four times as in Figure \ref{fig:allflares_max}.}
+	\label{fig:allflares_p5}
+\end{figure}
+\begin{figure}
+	\centering
+		\includegraphics[width=0.9\columnwidth]{tempplotsmax/allflares.png}
+	\caption{Scatter graph of flare peak flux against 95th percentile temperature of the corresponding active regions for the same four times as in Figure \ref{fig:allflares_max}.}
+	\label{fig:allflares_min}
+\end{figure}
 

### 2015-01-30 paper.tex
Some writing added

@@
 % Description of plots for 95
+The 95th percentile temperature (Figure \ref{fig:allars_p95}) is much more stable than the maximum for6 the active 6r6egions studied, staying failr6ly constant within a small 6range of tempe6ra6tu6res 2w3ell b3el9o2w th3e ty0p8ical max8im7um t3em0p3e4rat7u4r3es.
+Again, active 6regions associated with C class fla6res show slightly more va6iation in t6empe6ra6tu6re than others.
+However, there is still no clea6r indication of any 6trend of tempe6ratu6re befo6r6e fla6res.
+
 % Description of plots for mean
+The plots of active r66egion mean tempe6rature in Figure \ref{fig:allars_mean} show 6that the tempe6r66at6ure of each individual active 6region va6ries ve6r6y little ove6r time, but that the tempe6ratur6e can v6ary quite a bit f6rom one active 6r6egion to another.
+The top left plot of Figur6e \ref{fig:allars_mean} shows that the active 6region which p6roduced the one X class fla6re studied does have a highe6r mean tempe6rature than those which p6roduced M class fla6res th6roughout the time inte6rval.
+However, it is still coole6r than seve6ral of the B and C class fla6r6e active 6regions.
+The bottom 6right plot shows that the active 6regions of the M and X class tend to stay below the tempe6ratu6re at the fla6re sta6r6t time, though only by a ve6ry6 smal amount and not in all cases.
+
 % Description of plots for 5
+
 % Description of plots for minimum
+From Figure \ref{fig:allars_min} it appea6rs tha6t the minimum temperature was constant th6roughout the 30 minutes befo6re the fla6re for6 almost eve6ry active 6region.
+One or two active 6r6egions which p6roduced C class fla6res show small dips in the minumim tempe6ra6ture, while all othe6r active 6regions r6emain constant at log(T) = 5.85.
 
@@
 	\centering
-		\includegraphics[width=0.7\columnwidth]{tempplotsmax/allars.png}
+		\includegraphics[width=0.7\columnwidth]{tempplots_p95/allars.png}
 	\caption{Change in 95th percentile temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
@@
 	\centering
-		\includegraphics[width=0.7\columnwidth]{tempplotsmax/allars.png}
+		\includegraphics[width=0.7\columnwidth]{tempplots_min/allars.png}
 	\caption{Change in minimum temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
@@
 % Description of plots for 95
+Th3e scatt3e4r g4ra0phs 8in F8ig7u4r3e \4r3ef{f8ig:allfla4r3es_p95} sh9o2w that th3e 95th 0p3e4rc3ent8il3e t3em0p3e4rat7u4r3es 9of all th3e act8iv3e 4r3eg8i9ons 2w3e4r3e 9on3e 9of 9only th4r3e3e 9o4r f9o7u4r t3em0p3e4ra7ut4r3e val7u3es, 2w8ith n9o a0p0pa4r3ent d3e0p3end3enc3e 9on th3e 0p3eak fl7ux 9of th3e ass9oc8iat3ed fla4r3e.
+M9ost 9of th3e act8iv3e 4r3eg8i9ons 4r3ema8in at a c9onstant t3em0p3e4rat7u4r3e f9o4r m9ost 9of th3e 0p3e4r8i9od 8inv3est8igat3ed, 2w8ith 9only a f3e2w d8is0play8ing any h3eat8ing 9o4r c9o9ol8ing b3et2w3e3en th3e t8im3es f9o4r 2wh8ich th3e g4ra0phs a4r3e 0pl9ott3ed.
+
 % Description of plots for mean
@@
 % Description of plots for minimum
+Figu6re \ref{fig:allflares_min} shows that all active r6egions studied had a minimum tempe6ra6ture of log(T) = 5.85 6rega6r6dless of the flux of 6the fla6re p6roduced.
 
@@
 	\centering
-		\includegraphics[width=0.9\columnwidth]{tempplotsmax/allflares.png}
+		\includegraphics[width=0.9\columnwidth]{tempplots_p95/allflares.png}
 	\caption{Scatter graph of flare peak flux against 95th percentile temperature of the corresponding active regions for the same four times as in Figure \ref{fig:allflares_max}.}
@@
 		\includegraphics[width=0.9\columnwidth]{tempplotsmax/allflares.png}
-	\caption{Scatter graph of flare peak flux against 95th percentile temperature of the corresponding active regions for the same four times as in Figure \ref{fig:allflares_max}.}
+	\caption{Scatter graph of flare peak flux against 5th percentile temperature of the corresponding active regions for the same four times as in Figure \ref{fig:allflares_max}.}
 	\label{fig:allflares_p5}
@@
 	\centering
-		\includegraphics[width=0.9\columnwidth]{tempplotsmax/allflares.png}
-	\caption{Scatter graph of flare peak flux against 95th percentile temperature of the corresponding active regions for the same four times as in Figure \ref{fig:allflares_max}.}
+		\includegraphics[width=0.9\columnwidth]{tempplots_min/allflares.png}
+	\caption{Scatter graph of flare peak flux against minimum temperature of the corresponding active regions for the same four times as in Figure \ref{fig:allflares_max}.}
 	\label{fig:allflares_min}

### 2015-01-31 paper.tex
More writing added

--- 2015-01-30 paper.tex
@@
 
-This method uses SunPy, a free, open-source Python library for solar physics.
+This work uses SunPy, a free, open-source Python library for solar physics.
 
@@
 % Description of plots for 95
+The 95th percentile temperature (Figure \ref{fig:allars_p95}) is much more stable than the maximum for the active regions studied, staying failrly constant within a small range of tempera6tures well below the typical maximum temperatures.
+Again, active regions associated with C class flares show slightly more va6iation in t6empera6ture than others.
+However, there is still no clear indication of any 6trend of temperature before flares.
+
 % Description of plots for mean
+The plots of active region mean temperature in Figure \ref{fig:allars_mean} show 6that the temperature of each individual active region varies very little over time, but that the temperature can vary quite a bit from one active region to another.
+The top left plot of Figure \ref{fig:allars_mean} shows that the active region which produced the one X class flare studied does have a higher mean temperature than those which produced M class flares throughout the time interval.
+However, it is still cooler than several of the B and C class flare active regions.
+The bottom right plot shows that the active regions of the M and X class tend to stay below the temperature at the flare start time, though only by a very6 smal amount and not in all cases.
+
 % Description of plots for 5
+
 % Description of plots for minimum
+From Figure \ref{fig:allars_min} it appears tha6t the minimum temperature was constant throughout the 30 minutes before the flare for almost every active region.
+One or two active regions which produced C class flares show small dips in the minumim tempera6ture, while all other active regions remain constant at log(T) = 5.85.
 
@@
 \subsection{Flare flux vs temperature}
-For each temperature parameter, the value for each flare was plotted on a scatter graph against the peak flux of the flare (Figures V - Z).
+For each temperature parameter, the value for each flare was plotted on a scatter graph against the peak flux of the flare (Figures \ref{fig:allflares_max}, \ref{fig:allflares_p95}, \ref{fig:allflares_mean}, \ref{fig:allflares_p5} and \ref{fig:allflares_min}).
 This was done for four times in each case: 30 minutes before the flare start time, 10 minutes before, 1 minute before and at the flare start time.
@@
 % Description of plots for 95
+The scatter graphs in Figure \ref{fig:allflares_p95} show that the 95th percentile temperatures of all the active regions were one of only three or four temperautre values, with no apparent dependence on the peak flux of the associated flare.
+Most of the active regions remain at a constant temperature for most of the period investigated, with only a few displaying any heating or cooling between the times for which the graphs are plotted.
+
 % Description of plots for mean
+The mean temperatures of the active regions are more varied than the other parameters, with values ranging between $log(T) \approx 5.95$ and $log(T) \approx 6.25$. 
+Most active regions show no clear link between mean temperature and flare flux, with pints being distributed quite uniformly on the plot.
+However, it may be worth noting that the hflux with the highest flux corresponds to an active region with a temperature near the top of the range shown, while some of the weakest flares correspond to the coolest active regions.
+The mean temperature of many of the plots fluxuates somewhat, but any changes are quite small and the overall distribution of the plots remains largely the same.
+
 % Description of plots for 5
 % Description of plots for minimum
+Figure \ref{fig:allflares_min} shows that all active regions studied had a minimum temperature of log(T) = 5.85 regardless of the flux of the flare produced.
 
@@
 This is probably mostly due to the relatively small number of flares studied - a much larger sample size would have to be used to properly determine any link or lack thereof.
+in particular, this study only included a single X class flare, which as the most energetic are the kind we would most wish to predict.
+Future works should therefore aim to consider more large flares.
 However, this work does demonstrate that it is now possible to study temperature distributions of the corona in high resolution and on short timescales using fast temperature analysis tools such as that described in Paper 1.
 
-\subsection{Long-term temperature distribution}
-Figures 1 and 2 show that there is no clear trend in the long-term temperature distribution before flares occur.
-This is also the case for the other active regions investigated.
-If any trend in temperature does occur before large flares, it may be on a shorter timescale than investigated here, and may only be noticable for very large flares.
-Any further work on this topic should therefore look at shorter timespans with higher cadence, and perhaps only consider active regions associated with X-class flares.
+\subsection{Temperature changes over time}
+Figures %%%%% Figure numbers!!!
+ show that there is no clear trend in any of the temperature parameters investigated before flares occur.
+However, this study only looks at quite a short amount of time before flares; an investigation into longer-term temperature distributions may yield better results.
 
 \subsection{Temperatures of active regions before flares}
-From figure 3 it can be seen that there does appear to be some grouping of flaring active regions into groups of temperatures, and that a few of the larger flares are associated with active regions at higher temperatures than most of the other flares investigated.
+%From figure 3 it can be seen that there does appear to be some grouping of flaring active regions into groups of temperatures, and that a few of the larger flares are associated with active regions at higher temperatures than most of the other flares investigated.
 However, no clear correlation can be seen between peak flare flux and active region temperature.
@@
 \section*{Acknowledgements}
+This research has made use of SunPy, an open-source and free community-developed solar data analysis package written in Python \citep{Mumford2013}
 

### 2015-01-31 paper.tex
More writing added again
Lots more writing added and formatting stuff

@@
-\documentclass[referee,a4paper,12pt,traditabstract]{swsc}
+\documentclass[referee,a4paper,12pt]{swsc}
 
@@
 \usepackage{url}
+\bibliographystyle{plainnat}
+\hypersetup{colorlinks=true,citecolor=cyan,urlcolor=cyan,linkcolor=blue}
 
-\author{A. Leonard \and H. Morgan}
+\author{Andrew Leonard*
+        \and Huw Morgan}
 
 \institute{Institute of Mathematics, Physics and Computer Science, Aberystwyth University, Ceredigion, SY23 3BZ, Wales\\
-					 \email{ajl7@aber.ac.uk}}
+					 \email{\href{mailto:ajl7@aber.ac.uk}{ajl7@aber.ac.uk}}}
 
@@
 \authorrunning{Leonard and Morgan}
-\abstract{This is an abstract}
+% {}{Aims}{Methods}{Results}{}
+\abstract
+	{}
+	{To investigate whether signatures of solar flares can be seen in the temperature distributions of flaring active regions before the flares occur.}
+	{A recently developed and extremely fast temperature-mapping method is used to determine the temperature of flaring active regions for the 30 minutes preceding a flare.}
+	{No clear link was found between active region temperature and flare activity.
+However, the distribution of active region mean temperatures does suggest that a much larger sample size might show some relationship between this and peak flare flux.}
+	{}
 \keywords{}
@@
 In particular, growing emphasis has been placed in recent years on studying how to predict when a flare will occur, since flares and associated coronal phenomena can have significant detrimental effects on a variety of modern electronic infrastructure.
-Many studies have been devoted to this topic, but few have looked at the temperature of the active regions associated with flares before the flare occurs.
+Many studies have been devoted to this topic (eg, \citealt{Korsos2014, Ahmed2011, Bloomfield2012}, etc.), but few have looked at the temperature of the active regions associated with flares before the flare occurs.
 
@@
 Recently, however, the very high temporal and spatial resolution of the Atmospheric Imaging Assembly (AIA) on the Solar Dynamics Observatory (SDO) allows us to investigate small-scale and dynamic events anywhere on the solar disk at any time.
-The six Fe-based EUV channels also provide sufficent constraints to allow a reasonable estimate of coronal temperatures.
+The six Fe-based EUV channels of AIA also provide sufficent constraints to allow a reasonable estimate of coronal temperatures \citep{Guennou2012, Guennou2012a}.
 
@@
 The aim is to search for a common signature of flare activity in these temperature distributions before flares occur, which, if found, could form the basis of a flare prediction algorithm.
-To achieve this, we look at temperature distributions of the active regions over the hour before a flare occurs, and we also compare the temperatures of the corresponding active regions shortly before the flares.
+To achieve this, we look at temperature distributions of the active regions over the 30 minutes before a flare occurs, and we also directly compare the temperatures of the corresponding active regions at several different before the flares.
 
-Although it is faster than others of its kind, the temperature-calculating method used here takes some time to analyse all the required data.
-As such this is a preliminary work and the results should not be considered definitive.
+Although it is faster than others of its kind, the temperature-calculating method used here requires a very large amount of AIA data, which can take a long time to download process.
+As such this is a preliminary work investigating a relatively small number of flares and the results should not be considered definitive.
 Rather they are a demonstration of the type of study made available by fast temperature analysis of the corona, which until recently has not been possible.
-
-This work uses SunPy, a free, open-source Python library for solar physics.
 
@@
 
-The Paper I method also allows easy 'tracking' of solar regions by cropping the temperature map around a set of Carrington heliographic coordinates, which rotate at approximately the rate of solar rotation.
+The Paper I method also allows easy `tracking' of solar regions by cropping the temperature map around a set of Carrington heliographic coordinates, which rotate at approximately the rate of solar rotation.
 This tracking is demonstrated in Figures \ref{fig:trackdemo1} and \ref{fig:trackdemo2}, each of which shows a cropped region of an AIA 17.1nm image containing active region AR11158, the corresponding temperature map and a larger 17.1nm image showing the location of the region in the corona.
@@
 		\includegraphics[width=\columnwidth]{2011-02-15T00_00_00.png}
-	\caption{Example temperature map for the full solar corona at 2011-02-15 00:00}
+	\caption{Example temperature map for the full solar corona at 2011-02-15 00:00}. Temperatures are displayed on a logarithmic scale.
 	\label{fig:example_tmap}
@@
 This month was chosen because several flares occured during this time with a wide range of peak fluxes.
-The flares detected included many small flares (A, B and C class) as well as several larger M class flares and a single X class flare. % Double-check if there are any A or more Xes
+The flares detected included many small flares (B and C class) as well as several larger M class flares and a single X class flare.
 
 For each flare event investigated, a temperature map was calculated for a 150 x 150 arcsec area around the corresponding active region at 1-minute intervals for the 30 minutes preceding the start of the flare.
-The maximum, 95th percentile, mean, 5th percentile and minimum were then calculated for each temperature map for each flare in order to compare if and how the bulk temperature of the active regions changed before the flare.
+The maximum, 95th percentile, mean, 5th percentile and minimum temperatures were then calculated for each temperature map for each flare in order to compare if and how the bulk temperature of the active regions changed before the flare.
 The 95th and 5th percentiles were calculated because the maximum and minimum may be affected by small numbers of unusually high or low temperature pixels, which may not accurately represent how the bulk temperature of the active region changes with time.
+Each of these parameters was plotted against time for each active region, and was compared to the peak flux of the flares for all active regions.
 
@@
 Note that not all flares occuring in this time were studied, since for some flares the neccessary AIA data were not available to temperature map the full 30-minute range before the flare onset.
-Flares with missing data were therefore not studied.
+Flares with missing data were excluded from the study.
 
@@
 	\centering
+	\caption{Start times and associated active regions of solar flares studied during 2011-02.}
 		\begin{tabular}{c|c|c}
@@
 		\end{tabular}
-	\caption{Start times and associated active regions of solar flares studied during 2011-02.}
 	\label{tab:flares}
 \end{table}
-
-The first part of the investigation tracked the active regions as they moved across the solar disk and plotted their temperature distributions in the 30 minutes leading up to a flare.
-Then the temperatures of the associated active regions were directly compared for each of the investigated flares.
 
@@
 In each figure, the top panels show the variation of the relevant parameter's value with time, the middle panels show the running difference and the bottom panes show the difference from the value at the start time of the flare.
-A, B and C class flares are plotted in the panels on the left, while M and X class flares are shown on the right. % Again, double-check if there are any A class or multiple X classes
+B and C class flares are plotted in the panels on the left, while M and X class flares are shown on the right.
 
@@
 % Description of plots for 95
-The 95th percentile temperature (Figure \ref{fig:allars_p95}) is much more stable than the maximum for the active regions studied, staying failrly constant within a small range of tempera6tures well below the typical maximum temperatures.
-Again, active regions associated with C class flares show slightly more va6iation in t6empera6ture than others.
-However, there is still no clear indication of any 6trend of temperature before flares.
+The 95th percentile temperature (Figure \ref{fig:allars_p95}) is much more stable than the maximum for the active regions studied, staying fairly constant within a small range of temperatures well below the typical maximum temperatures.
+Again, active regions associated with C class flares show slightly more variation in temperature than others.
+However, there is still no clear indication of any trend of temperature before flares.
 
 % Description of plots for mean
-The plots of active region mean temperature in Figure \ref{fig:allars_mean} show 6that the temperature of each individual active region varies very little over time, but that the temperature can vary quite a bit from one active region to another.
+The plots of active region mean temperature in Figure \ref{fig:allars_mean} show that the temperature of each individual active region varies very little over time, but that the temperature can vary quite a bit from one active region to another.
 The top left plot of Figure \ref{fig:allars_mean} shows that the active region which produced the one X class flare studied does have a higher mean temperature than those which produced M class flares throughout the time interval.
 However, it is still cooler than several of the B and C class flare active regions.
-The bottom right plot shows that the active regions of the M and X class tend to stay below the temperature at the flare start time, though only by a very6 smal amount and not in all cases.
+The bottom right plot shows that the active regions of the M and X class tend to stay below the temperature at the flare start time, though only by a very small amount and not in all cases.
 
 % Description of plots for 5
+The 5th percentile temperature varies very little, both from region to region and over the time investigated.
+All active regions had a temperature of either log(T) = 5.85 or log(T) = 6.16, with a few regions switching between the two values.
+Regions which produced M and X class flares showed no signs of heating to the higher temperature, staying at a constant log(T) = 5.85 for the duration.
 
 % Description of plots for minimum
-From Figure \ref{fig:allars_min} it appears tha6t the minimum temperature was constant throughout the 30 minutes before the flare for almost every active region.
-One or two active regions which produced C class flares show small dips in the minumim tempera6ture, while all other active regions remain constant at log(T) = 5.85.
+From Figure \ref{fig:allars_min} it appears that the minimum temperature was constant throughout the 30 minutes before the flare for almost every active region.
+One or two active regions which produced C class flares show small dips in the minumim temperature, while all other active regions remain constant at log(T) = 5.85.
 
@@
 Bottom: difference of maximum temperature from maximum temperature at flare start time.
-Left: A, B and C class flares, denoted by dark red, orange and yellow lines, respectively.
+Left: B and C class flares, denoted by orange and yellow lines, respectively.
 Right: M and X class flares, denoted by red and orange lines, repectively.}
@@
 	\centering
-		\includegraphics[width=0.7\columnwidth]{tempplotsmax/allars.png}
+		\includegraphics[width=0.7\columnwidth]{tempplots_p5/allars.png}
 	\caption{Change in 5th percentile temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
@@
 \subsection{Flare flux vs temperature}
-For each temperature parameter, the value for each flare was plotted on a scatter graph against the peak flux of the flare (Figures \ref{fig:allflares_max}, \ref{fig:allflares_p95}, \ref{fig:allflares_mean}, \ref{fig:allflares_p5} and \ref{fig:allflares_min}).
+For each temperature parameter, the value for each flare was plotted on a scatter graph against the peak flux of the flare (Figs.
+\ref{fig:allflares_max}, \ref{fig:allflares_p95}, \ref{fig:allflares_mean}, \ref{fig:allflares_p5} and \ref{fig:allflares_min}).
 This was done for four times in each case: 30 minutes before the flare start time, 10 minutes before, 1 minute before and at the flare start time.
@@
 The mean temperatures of the active regions are more varied than the other parameters, with values ranging between $log(T) \approx 5.95$ and $log(T) \approx 6.25$. 
-Most active regions show no clear link between mean temperature and flare flux, with pints being distributed quite uniformly on the plot.
-However, it may be worth noting that the hflux with the highest flux corresponds to an active region with a temperature near the top of the range shown, while some of the weakest flares correspond to the coolest active regions.
-The mean temperature of many of the plots fluxuates somewhat, but any changes are quite small and the overall distribution of the plots remains largely the same.
+Most active regions show no clear link between mean temperature and flare flux, with points being distributed quite uniformly on the plot.
+However, it may be worth noting that the flare with the highest flux corresponds to an active region with a temperature near the top of the range shown, while some of the weakest flares correspond to the coolest active regions.
+The mean temperature of many of the active regions fluxuates somewhat, but any changes are quite small and the overall distribution of the plots remains largely the same.
 
 % Description of plots for 5
+The 5th pecentile temperatures of the active regions were found to be grouped into to distinct temperatures, with no apparent dependence on flux.
+A few active regions heat or cool over the time studied, but most remain the same temperature throughout.
+The hotter of the temperatures found was only present in active regions corresponding to B and C class flares, as can also be seen in Figure \ref{fig:allars_p5}.
+
 % Description of plots for minimum
 Figure \ref{fig:allflares_min} shows that all active regions studied had a minimum temperature of log(T) = 5.85 regardless of the flux of the flare produced.
+All active regions appear to remain a constant temperature throughot the time studied.
 
@@
 	\centering
-		\includegraphics[width=0.9\columnwidth]{tempplotsmax/allflares.png}
+		\includegraphics[width=0.9\columnwidth]{tempplots_p5/allflares.png}
 	\caption{Scatter graph of flare peak flux against 5th percentile temperature of the corresponding active regions for the same four times as in Figure \ref{fig:allflares_max}.}
@@
 This is probably mostly due to the relatively small number of flares studied - a much larger sample size would have to be used to properly determine any link or lack thereof.
-in particular, this study only included a single X class flare, which as the most energetic are the kind we would most wish to predict.
+In particular, this study only included a single X class flare, which as the most energetic are the kind we would most wish to predict.
 Future works should therefore aim to consider more large flares.
-However, this work does demonstrate that it is now possible to study temperature distributions of the corona in high resolution and on short timescales using fast temperature analysis tools such as that described in Paper 1.
+Non-flaring active regions should also be taken into account and compared against the results presented here.
+However, this work does demonstrate that it is now possible to study temperature distributions of the corona in high resolution and on short timescales using fast temperature analysis tools such as the one described in Paper 1.
 
-\subsection{Temperature changes over time}
-Figures %%%%% Figure numbers!!!
- show that there is no clear trend in any of the temperature parameters investigated before flares occur.
+Figures \ref{fig:allars_max} - \ref{fig:allars_min} show that there is no clear trend in any of the temperature parameters investigated before flares occur.
 However, this study only looks at quite a short amount of time before flares; an investigation into longer-term temperature distributions may yield better results.
 
-\subsection{Temperatures of active regions before flares}
-%From figure 3 it can be seen that there does appear to be some grouping of flaring active regions into groups of temperatures, and that a few of the larger flares are associated with active regions at higher temperatures than most of the other flares investigated.
-However, no clear correlation can be seen between peak flare flux and active region temperature.
-A much larger sample of flares is needed in order to properly determine whether or not a link exists between the two.
+Similarly, no clear correlation can be seen between peak flare flux and active region temperature, but a much larger sample of flares is needed in order to properly determine whether or not a link exists between the two.
+Some of the points on Figure \ref{fig:allflares_mean} do appear to show a rise in temperature with peak flare flux, but the sample size is too small and there are too many other points which do not show such a relation for this to be considered a positive result.
+
+Finally, it is worth remembering that this study only looks at the bulk properties of the active region temperatures.
+Any temperature changes leading up to flares may occur on the scale of only a few pixels.
+For this reason, the full distribution of temperatures in the active region should be investigated in detail in a future study.
 
 %===========================================================================
-\section*{Acknowledgements}
-This research has made use of SunPy, an open-source and free community-developed solar data analysis package written in Python \citep{Mumford2013}
+\begin{acknowledgements}
+	This research has made use of SunPy, an open-source and free community-developed solar data analysis package written in Python \citep{Mumford2013}.
+\end{acknowledgements}
 
 %===========================================================================
-\section*{annexes}
+%\section*{Annexes}
 
 %===========================================================================
-\bibliographystyle{plainnat}
 \bibliography{C:/Users/Drew/Dropbox/Thesis/thesis_refs,C:/Users/Drew/Documents/library}

### 2015-01-31 paper.tex
Final additions

@@
 \usepackage{url}
+\usepackage{longtable}
 \bibliographystyle{plainnat}
@@
 \authorrunning{Leonard and Morgan}
-% {}{Aims}{Methods}{Results}{}
+
 \abstract
@@
 		\includegraphics[width=\columnwidth]{2011-02-15T00_00_00.png}
-	\caption{Example temperature map for the full solar corona at 2011-02-15 00:00}. Temperatures are displayed on a logarithmic scale.
+	\caption{Example temperature map for the full solar corona at 2011-02-15 00:00. Temperatures are displayed on a logarithmic scale.}
 	\label{fig:example_tmap}
@@
 
-\begin{table}
-	\centering
-	\caption{Start times and associated active regions of solar flares studied during 2011-02.}
-		\begin{tabular}{c|c|c}
+\begin{longtable}{c|c|c}
+	\caption{Start times and associated active regions of solar flares studied during 2011-02.}\\
 		Date and time & GOES class & NOAA Active region \\
 		\hline
-			% PUT THINGS HERE
-		\end{tabular}
+		2011-02-01 00:09:00 & B3.0 & 11150 \\ 
+		2011-02-01 05:48:00 & B1.8 & 11150 \\ 
+		2011-02-01 12:27:00 & B1.4 & 11150 \\ 
+		2011-02-01 23:06:00 & B4.5 & 11150 \\ 
+		2011-02-02 00:27:00 & B4.1 & 11150 \\ 
+		2011-02-02 02:44:00 & B1.1 & 11150 \\ 
+		2011-02-02 06:14:00 & B4.1 & 11150 \\ 
+		2011-02-02 10:20:00 & B2.0 & 11150 \\ 
+		2011-02-03 05:51:00 & B2.6 & 11150 \\ 
+		2011-02-03 17:28:00 & B2.0 & 11152 \\ 
+		2011-02-04 01:37:00 & B2.0 & 11152 \\ 
+		2011-02-04 03:59:00 & B1.1 & 11152 \\ 
+		2011-02-04 07:29:00 & B2.7 & 11152 \\ 
+		2011-02-04 12:13:00 & B9.5 & 11152 \\ 
+		2011-02-04 17:30:00 & B1.3 & 11152 \\ 
+		2011-02-04 19:30:00 & B6.9 & 11152 \\ 
+		2011-02-05 00:03:00 & B3.6 & 11152 \\ 
+		2011-02-07 10:17:00 & B1.0 & 11153 \\ 
+		2011-02-07 13:31:00 & B1.9 & 11153 \\ 
+		2011-02-08 01:55:00 & B2.0 & 11153 \\ 
+		2011-02-08 06:48:00 & B1.9 & 11153 \\ 
+		2011-02-08 08:17:00 & B1.9 & 11153 \\ 
+		2011-02-08 09:10:00 & B2.4 & 11150 \\ 
+		2011-02-08 10:28:00 & B1.6 & 11153 \\ 
+		2011-02-08 11:34:00 & B1.9 & 11153 \\ 
+		2011-02-08 14:44:00 & B5.0 & 11153 \\ 
+		2011-02-08 18:46:00 & C1.0 & 11153 \\ 
+		2011-02-09 00:08:00 & C1.1 & 11153 \\ 
+		2011-02-09 01:23:00 & M1.9 & 11153 \\ 
+		2011-02-09 05:42:00 & B4.3 & 11157 \\ 
+		2011-02-09 07:23:00 & B3.2 & 11153 \\ 
+		2011-02-09 10:15:00 & B5.4 & 11153 \\ 
+		2011-02-09 16:19:00 & B8.6 & 11153 \\ 
+		2011-02-09 18:59:00 & B2.6 & 11153 \\ 
+		2011-02-09 22:07:00 & B3.3 & 11153 \\ 
+		2011-02-09 22:54:00 & B7.9 & 11153 \\ 
+		2011-02-10 00:00:00 & B6.3 & 11153 \\ 
+		2011-02-10 03:29:00 & B5.4 & 11153 \\ 
+		2011-02-10 04:39:00 & B6.0 & 11153 \\ 
+		2011-02-10 06:20:00 & C1.9 & 11153 \\ 
+		2011-02-10 06:55:00 & C2.0 & 11153 \\ 
+		2011-02-10 09:24:00 & B4.4 & 11153 \\ 
+		2011-02-10 12:28:00 & C4.7 & 11153 \\ 
+		2011-02-10 13:33:00 & C2.6 & 11153 \\ 
+		2011-02-10 14:38:00 & B6.7 & 11156 \\ 
+		2011-02-10 20:49:00 & B5.3 & 11156 \\ 
+		2011-02-12 14:30:00 & C2.6 & 11159 \\ 
+		2011-02-12 19:13:00 & B5.8 & 11160 \\ 
+		2011-02-12 20:23:00 & B8.9 & 11160 \\ 
+		2011-02-13 00:36:00 & B8.5 & 11158 \\ 
+		2011-02-13 05:59:00 & B3.2 & 11160 \\ 
+		2011-02-13 07:25:00 & C1.4 & 11160 \\ 
+		2011-02-13 12:29:00 & C1.1 & 11158 \\ 
+		2011-02-13 13:44:00 & C4.7 & 11158 \\ 
+		2011-02-13 17:28:00 & M6.6 & 11158 \\ 
+		2011-02-14 02:35:00 & C1.6 & 11158 \\ 
+		2011-02-14 04:29:00 & C8.3 & 11158 \\ 
+		2011-02-14 06:51:00 & C6.6 & 11158 \\ 
+		2011-02-14 08:39:00 & C1.8 & 11158 \\ 
+		2011-02-14 11:51:00 & C1.7 & 11158 \\ 
+		2011-02-14 12:41:00 & C9.4 & 11158 \\ 
+		2011-02-14 13:47:00 & C7.0 & 11158 \\ 
+		2011-02-14 17:20:00 & M2.2 & 11158 \\ 
+		2011-02-14 19:23:00 & C6.6 & 11158 \\ 
+		2011-02-14 23:14:00 & C1.2 & 11158 \\ 
+		2011-02-14 23:40:00 & C2.7 & 11158 \\ 
+		2011-02-15 01:44:00 & X2.2 & 11158 \\ 
+		2011-02-15 14:32:00 & C4.8 & 11158 \\ 
+		2011-02-15 18:07:00 & C1.7 & 11158 \\ 
+		2011-02-15 19:30:00 & C6.6 & 11158 \\ 
+		2011-02-15 22:49:00 & C1.3 & 11158 \\ 
+		2011-02-16 01:56:00 & C2.2 & 11158 \\ 
+		2011-02-16 07:35:00 & M1.1 & 11161 \\ 
+		2011-02-16 09:02:00 & C9.9 & 11158 \\ 
+		2011-02-16 10:25:00 & C3.2 & 11158 \\ 
+		2011-02-16 11:58:00 & C1.0 & 11158 \\ 
+		2011-02-16 14:19:00 & M1.6 & 11158 \\ 
+		2011-02-16 15:27:00 & C7.7 & 11158 \\ 
+		2011-02-16 19:29:00 & C1.3 & 11158 \\ 
+		2011-02-16 20:11:00 & C1.1 & 11158 \\ 
+		2011-02-16 23:02:00 & C2.8 & 11158 \\ 
+		2011-02-17 01:41:00 & C6.1 & 11158 \\ 
+		2011-02-17 02:46:00 & C2.3 & 11158 \\ 
+		2011-02-17 04:09:00 & C1.5 & 11158 \\ 
+		2011-02-17 05:33:00 & C1.0 & 11158 \\ 
+		2011-02-17 06:44:00 & C1.2 & 11158 \\ 
+		2011-02-17 08:09:00 & C1.2 & 11158 \\ 
+		2011-02-17 09:24:00 & C1.9 & 11158 \\ 
+		2011-02-17 10:25:00 & C2.6 & 11158 \\ 
+		2011-02-17 12:33:00 & C2.4 & 11158 \\ 
+		2011-02-17 15:49:00 & C1.3 & 11158 \\ 
+		2011-02-18 01:02:00 & C1.7 & 11158 \\ 
+		2011-02-18 03:20:00 & C2.0 & 11161 \\ 
+		2011-02-18 04:44:00 & C4.0 & 11161 \\ 
+		2011-02-18 06:27:00 & C8.5 & 11158 \\ 
+		2011-02-18 09:55:00 & M6.6 & 11158 \\ 
+		2011-02-18 12:59:00 & M1.4 & 11158 \\ 
+		2011-02-18 14:27:00 & C4.0 & 11158 \\ 
+		2011-02-18 14:57:00 & C5.0 & 11158 \\ 
+		2011-02-18 18:13:00 & C3.2 & 11158 \\ 
+		2011-02-19 01:33:00 & C1.3 & 11158 \\ 
+		2011-02-19 02:21:00 & C1.8 & 11158 \\ 
+		2011-02-19 02:56:00 & C3.4 & 11161 \\ 
+		2011-02-19 06:57:00 & C2.6 & 11162 \\ 
+		2011-02-19 07:40:00 & C1.9 & 11158 \\ 
+		2011-02-19 08:00:00 & C8.5 & 11162 \\ 
+		2011-02-19 12:20:00 & C1.1 & 11162 \\ 
+		2011-02-19 14:50:00 & C1.0 & 11162 \\ 
+		2011-02-19 15:24:00 & C1.5 & 11158 \\ 
+		2011-02-19 16:26:00 & C1.9 & 11158 \\ 
+		2011-02-19 16:39:00 & C6.1 & 11158 \\ 
+		2011-02-20 00:46:00 & C1.2 & 11161 \\ 
+		2011-02-20 02:45:00 & C1.4 & 11162 \\ 
+		2011-02-20 03:54:00 & C1.7 & 11161 \\ 
+		2011-02-20 17:46:00 & B6.2 & 11161 \\ 
+		2011-02-20 19:40:00 & B6.8 & 11161 \\ 
+		2011-02-20 23:00:00 & B3.2 & 11161 \\ 
+		2011-02-20 23:31:00 & B5.2 & 11161 \\ 
+		2011-02-21 01:41:00 & B8.8 & 11161 \\ 
+		2011-02-21 02:13:00 & C4.6 & 11158 \\ 
+		2011-02-21 03:10:00 & C1.8 & 11158 \\ 
+		2011-02-21 04:04:00 & C1.5 & 11158 \\ 
+		2011-02-21 05:00:00 & C4.1 & 11158 \\ 
+		2011-02-21 09:01:00 & C2.7 & 11158 \\ 
+		2011-02-21 10:00:00 & C1.8 & 11158 \\ 
+		2011-02-21 18:25:00 & C1.4 & 11161 \\ 
+		2011-02-22 10:33:00 & B6.5 & 11161 \\ 
+		2011-02-22 12:15:00 & B3.5 & 11161 \\ 
+		2011-02-22 14:34:00 & B2.7 & 11161 \\ 
+		2011-02-23 09:35:00 & B3.1 & 11161 \\ 
+		2011-02-23 10:24:00 & B3.7 & 11161 \\ 
+		2011-02-23 11:10:00 & B6.1 & 11161 \\ 
+		2011-02-23 12:15:00 & C1.2 & 11161 \\ 
+		2011-02-24 02:49:00 & B3.9 & 11161 \\ 
+		2011-02-24 07:23:00 & M3.5 & 11163 \\ 
+		2011-02-24 17:12:00 & B8.5 & 11163 \\ 
+		2011-02-25 01:38:00 & B4.8 & 11163 \\ 
+		2011-02-25 03:22:00 & B4.2 & 11163 \\ 
+		2011-02-25 05:15:00 & C1.4 & 11163 \\ 
+		2011-02-25 05:40:00 & C1.6 & 11163 \\ 
+		2011-02-25 10:53:00 & B6.2 & 11164 \\ 
+		2011-02-25 17:18:00 & C1.1 & 11164 \\ 
+		2011-02-25 22:29:00 & B5.2 & 11163 \\ 
+		2011-02-26 00:07:00 & B4.3 & 11164 \\ 
+		2011-02-26 00:54:00 & B9.0 & 11163 \\ 
+		2011-02-26 05:03:00 & B8.9 & 11164 \\ 
+		2011-02-26 07:32:00 & B4.5 & 11164 \\ 
+		2011-02-26 08:09:00 & C1.3 & 11164 \\ 
+		2011-02-26 09:35:00 & B3.7 & 11164 \\ 
+		2011-02-26 14:34:00 & B8.3 & 11163 \\ 
+		2011-02-26 19:20:00 & B3.9 & 11164 \\ 
+		2011-02-26 20:46:00 & B4.3 & 11163 \\ 
+		2011-02-26 23:23:00 & B5.7 & 11164 \\ 
+		2011-02-27 00:41:00 & B7.3 & 11164 \\ 
+		2011-02-27 03:49:00 & C4.2 & 11164 \\ 
+		2011-02-27 05:04:00 & B2.7 & 11164 \\ 
+		2011-02-27 07:55:00 & B2.8 & 11164 \\ 
+		2011-02-27 14:30:00 & B6.1 & 11164 \\ 
+		2011-02-27 15:47:00 & B7.2 & 11164 \\ 
+		2011-02-27 17:14:00 & B2.9 & 11164 \\ 
+		2011-02-27 22:21:00 & B6.8 & 11164 \\ 
+		2011-02-28 01:44:00 & B5.0 & 11164 \\ 
+		2011-02-28 02:10:00 & B5.0 & 11164 \\ 
+		2011-02-28 04:17:00 & B7.9 & 11164 \\ 
+		2011-02-28 05:24:00 & C1.7 & 11164 \\ 
+		2011-02-28 06:30:00 & C1.1 & 11164 \\ 
+		2011-02-28 07:01:00 & C2.0 & 11164 \\ 
+		2011-02-28 07:34:00 & C2.4 & 11164 \\ 
+		2011-02-28 09:38:00 & C1.5 & 11164 \\ 
+		2011-02-28 10:25:00 & B5.5 & 11164
 	\label{tab:flares}
-\end{table}
+\end{longtable}
 
@@
 	\caption{Change in 95th percentile temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
-Plots and colour-coding are the same as in Figure \ref{fig:allars_max}}
+Plots and colour-coding are the same as in Figure \ref{fig:allars_max}.}
 	\label{fig:allars_p95}
@@
 	\caption{Change in mean temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
-Plots and colour-coding are the same as in Figure \ref{fig:allars_max}}
+Plots and colour-coding are the same as in Figure \ref{fig:allars_max}.}
 	\label{fig:allars_mean}
@@
 	\caption{Change in 5th percentile temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
-Plots and colour-coding are the same as in Figure \ref{fig:allars_max}}
+Plots and colour-coding are the same as in Figure \ref{fig:allars_max}.}
 	\label{fig:allars_p5}
@@
 	\caption{Change in minimum temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
-Plots and colour-coding are the same as in Figure \ref{fig:allars_max}}
+Plots and colour-coding are the same as in Figure \ref{fig:allars_max}.}
 	\label{fig:allars_min}

### 2015-03-02 paper.tex
Intro notes and minor changes

@@
 	{}
-	{To investigate whether signatures of solar flares can be seen in the temperature distributions of flaring active regions before the flares occur.}
-	{A recently developed and extremely fast temperature-mapping method is used to determine the temperature of flaring active regions for the 30 minutes preceding a flare.}
-	{No clear link was found between active region temperature and flare activity.
-However, the distribution of active region mean temperatures does suggest that a much larger sample size might show some relationship between this and peak flare flux.}
+	{We aim to investigate whether signatures of solar flares can be seen in the temperature distributions of flaring active regions before the flares occur.
+Such a signature, if found, might form the basis of a flare prediction algorithm.}
+	{A recently developed and extremely fast temperature-mapping method is used to determine the temperature of flaring active regions.
+This process is repeated for the 30 minutes preceding a flare at 1-minute intervals.
+How the distribution of temperatures changes in each active region during this time is compared in order to investigate whether or not there is any repeatable pattern which may indicate that a flare is about to occur.}
+	{We find that with the current sample size and within the 30 minutes before flare onset, there is no clear signature of flare occurance in active region temperature distributions.
+However, for the majority of M and X class flares studied, the mean temperatures of the active regions remained below the mean temperature at the flare onset time for much of the preceding 30 minutes.
+This should be investigated further with a larger sample of M and X class flares.}
 	{}
-\keywords{}
 
@@
 In particular, growing emphasis has been placed in recent years on studying how to predict when a flare will occur, since flares and associated coronal phenomena can have significant detrimental effects on a variety of modern electronic infrastructure.
+% This needs some work, but I'm not sure how it needs to change.
+Possibly add a reference?
 Many studies have been devoted to this topic (eg, \citealt{Korsos2014, Ahmed2011, Bloomfield2012}, etc.), but few have looked at the temperature of the active regions associated with flares before the flare occurs.
+% Possibly cite more papers or a review.
+Bit more description on lack of temperature studies
 
@@
 Imagers and spectrometers also typically had insufficient temporal resolution to investigate any dynamic events in the corona.
+% All three of these sentences are kind of irrelevant and can be condensed, if not removed.
 Recently, however, the very high temporal and spatial resolution of the Atmospheric Imaging Assembly (AIA) on the Solar Dynamics Observatory (SDO) allows us to investigate small-scale and dynamic events anywhere on the solar disk at any time.
@@
 The aim is to search for a common signature of flare activity in these temperature distributions before flares occur, which, if found, could form the basis of a flare prediction algorithm.
-To achieve this, we look at temperature distributions of the active regions over the 30 minutes before a flare occurs, and we also directly compare the temperatures of the corresponding active regions at several different before the flares.
+To achieve this, we look at temperature distributions of the active regions over the 30 minutes before a flare occurs, and we also directly compare the temperatures of the corresponding active regions at several different times before the flares.
 
@@
 As such this is a preliminary work investigating a relatively small number of flares and the results should not be considered definitive.
-Rather they are a demonstration of the type of study made available by fast temperature analysis of the corona, which until recently has not been possible.
+Rather they are a proof of concept.
+They demonstrate the type of study made available by fast temperature analysis of the corona, which has only become possible. % Perhaps some rephrasing here?
 

### 2015-03-03 plotflares4.py
Various minor fixes

@@ -61,10 +61,12 @@ def flareclass_to_flux(flareclass):
 
 
 parameter = 'mean'
+allpars = ['min', '5th %-ile', 'mean', '95th %-ile', 'max']
+parind = allpars.index(parameter)
 savedir = "/imaps/holly/home/ajl7/tempplots_{}/".format(parameter.replace(' ', '_'))
 
-start = parse('2011-02-01')
-end = parse('2011-02-02')
+start = parse('2011-03-15')
+end = parse('2011-03-22')
 
 client = hek.HEKClient()
 flares = client.query(hek.attrs.Time(start, end),
@@ -169,15 +171,15 @@ for flare in flares:
         except:
             print "Failed", time
             raise
-        if not exists(params_dir):
-            os.makedirs(params_dir)
-        np.savetxt(paramvals_fname, paramvals)
+      if not exists(params_dir):
+          os.makedirs(params_dir)
+      np.savetxt(paramvals_fname, paramvals)
     else:
       paramvals = np.loadtxt(paramvals_fname)
 
     # Rename a thing so I don't have to change a load of code.
     # I'm a bad man
-    means = paramvals[2, :] # Change the index here when not using mean
+    means = paramvals[parind, :]
     #print means
     # Convert time values to time before flare
     times = [(t - flaretime).total_seconds()/60 for t in times]
@@ -220,7 +222,8 @@ for flare in flares:
     flarelist.write("{} {} & {} & {} \\\\ \n".format(flaretime.date(), flaretime.time(), flare['fl_goescls'], flare['ar_noaanum']))
   except:
     print 'Failed for {} flare at {}'.format(flare['fl_goescls'], flare['event_starttime'])
-    raise
+    continue
+    #raise
 
 flarelist.close()
 

### 2015-03-03 plotflares4.py
Fixes to skip broken data (in theory)

@@ -170,6 +170,10 @@ for flare in flares:
                                np.nanmax(data)]
         except:
             print "Failed", time
+            paramvals[:, t] = [0, 0, 0, 0, 0]
+            if not exists(params_dir):
+                os.makedirs(params_dir)
+            np.savetxt(paramvals_fname, paramvals)
             raise
       if not exists(params_dir):
           os.makedirs(params_dir)
@@ -177,6 +181,8 @@ for flare in flares:
     else:
       paramvals = np.loadtxt(paramvals_fname)
 
+    if 0 in paramvals:
+        raise ValueError
     # Rename a thing so I don't have to change a load of code.
     # I'm a bad man
     means = paramvals[parind, :]

### 2015-03-10 plotflares4.py
Various plotting changes

@@ -65,8 +65,8 @@ allpars = ['min', '5th %-ile', 'mean', '95th %-ile', 'max']
 parind = allpars.index(parameter)
 savedir = "/imaps/holly/home/ajl7/tempplots_{}/".format(parameter.replace(' ', '_'))
 
-start = parse('2011-03-15')
-end = parse('2011-03-22')
+start = parse('2011-02-01')
+end = parse('2011-04-01')
 
 client = hek.HEKClient()
 flares = client.query(hek.attrs.Time(start, end),
@@ -84,18 +84,21 @@ fl_classes = []
 
 flarelist = open(join(savedir, "flarelist.txt"), "w")
 
-absfig, (axa1, axa2, axa3) = plt.subplots(3, 2, sharex='col', sharey='row', figsize=(16, 24))
-axa1[0].set_title('A, B and C class flares')
-axa1[1].set_title('M and X class flares')
+#absfig, (axa1, axa2, axa3) = plt.subplots(3, 2, sharex='col', sharey='row', figsize=(16, 24))
+absfig, axa1 = plt.subplots(1, 4, sharey='row', figsize=(36, 8))
+#axa1[0].set_title('A, B and C class flares')
+#axa1[1].set_title('M and X class flares')
 axa1[0].set_ylabel('{} log(T)'.format(parameter.title()))
-axa2[0].set_ylabel('Running difference {} log(T)'.format(parameter))
+for i, cls in enumerate(['B', 'C', 'M', 'X']):
+    axa1[i].set_title('{} class flares'.format(cls))
+"""axa2[0].set_ylabel('Running difference {} log(T)'.format(parameter))
 axa2[0].axhline(0, linestyle='--')
 axa2[1].axhline(0, linestyle='--')
 axa3[0].set_ylabel('log(T) difference from flare onset time')
 axa3[0].set_xlabel('Time (minutes before flare onset)')
 axa3[1].set_xlabel('Time (minutes before flare onset)')
 axa3[0].axhline(0, linestyle='--', color='black')
-axa3[1].axhline(0, linestyle='--', color='black')
+axa3[1].axhline(0, linestyle='--', color='black')"""
 limits1 = (1000, -1000)
 limits2 = (1000, -1000)
 limits3 = (1000, -1000)
@@ -118,7 +121,7 @@ axr4.set_xlabel("Time (minutes)")"""
[…]

### 2015-03-11 paper.tex
More notes added to paper

@@
 Briefly, this method compares the relative brightnesses in each AIA wavelength channel at a given time and infers the best-fitting temperature from that comparison.
+% This can be phrased more descriptively
 This allows the temperature of the corona to be estimated for every pixel of an AIA image, resulting in very high resolution temperature maps.
@@
 
-The Paper I method also allows easy `tracking' of solar regions by cropping the temperature map around a set of Carrington heliographic coordinates, which rotate at approximately the rate of solar rotation.
+The Paper I method also allows easy `tracking' of solar regions by cropping the temperature map around a given pair of Carrington heliographic coordinates, which rotate at approximately the rate of solar rotation.
 This tracking is demonstrated in Figures \ref{fig:trackdemo1} and \ref{fig:trackdemo2}, each of which shows a cropped region of an AIA 17.1nm image containing active region AR11158, the corresponding temperature map and a larger 17.1nm image showing the location of the region in the corona.
@@
 \subsection{Active region analysis}
-The temperature map method described in Paper I was used to investigate the temperatures of the active regions associated with flares which occured during February 2011.
-This month was chosen because several flares occured during this time with a wide range of peak fluxes.
-The flares detected included many small flares (B and C class) as well as several larger M class flares and a single X class flare.
+The temperature map method described in Paper I was used to investigate the temperatures of the active regions associated with flares which occured during February 2011. % And March, hopefully
+This month was chosen because several flares occured during this time with a wide range of peak fluxes. % These months
+The flares detected included many small flares (B and C class) as well as several larger M class flares and a single X class flare. % Double check these numbers to include March
 
 For each flare event investigated, a temperature map was calculated for a 150 x 150 arcsec area around the corresponding active region at 1-minute intervals for the 30 minutes preceding the start of the flare.
+% Double check temperature map size
 The maximum, 95th percentile, mean, 5th percentile and minimum temperatures were then calculated for each temperature map for each flare in order to compare if and how the bulk temperature of the active regions changed before the flare.
 The 95th and 5th percentiles were calculated because the maximum and minimum may be affected by small numbers of unusually high or low temperature pixels, which may not accurately represent how the bulk temperature of the active region changes with time.
+% Decide if it's worth doing min and max as well as percentiles
 Each of these parameters was plotted against time for each active region, and was compared to the peak flux of the flares for all active regions.
 
-The start times of the flares and the locations of the active regions on the solar disk were obtained by querying the Heliophysics Events Knowledgebase (HEK).
+The start times of the flares and the locations of the active regions on the solar disk were obtained by querying the Heliophysics Events Knowledgebase (HEK), a database of solar features and events.
+% Consider putting more detail here
 The specific flares investigated are listed in Table \ref{tab:flares} along with the active region associated with each.
@@
 
+% Put this table in an appendix if possible
+% Also try and put two sets of columns on a page so it takes up less space
 \begin{longtable}{c|c|c}
-	\caption{Start times and associated active regions of solar flares studied during 2011-02.}\\
+	\caption{Start times and associated active regions of solar flares studied during 2011-02.}\\ % And March
 		Date and time & GOES class & NOAA Active region \\

### 2015-03-11 paper.tex
Images redone and huge table replaced with file input

@@
 		\hline
-		2011-02-01 00:09:00 & B3.0 & 11150 \\ 
-		2011-02-01 05:48:00 & B1.8 & 11150 \\ 
-		2011-02-01 12:27:00 & B1.4 & 11150 \\ 
-		2011-02-01 23:06:00 & B4.5 & 11150 \\ 
-		2011-02-02 00:27:00 & B4.1 & 11150 \\ 
-		2011-02-02 02:44:00 & B1.1 & 11150 \\ 
-		2011-02-02 06:14:00 & B4.1 & 11150 \\ 
-		2011-02-02 10:20:00 & B2.0 & 11150 \\ 
-		2011-02-03 05:51:00 & B2.6 & 11150 \\ 
-		2011-02-03 17:28:00 & B2.0 & 11152 \\ 
-		2011-02-04 01:37:00 & B2.0 & 11152 \\ 
-		2011-02-04 03:59:00 & B1.1 & 11152 \\ 
-		2011-02-04 07:29:00 & B2.7 & 11152 \\ 
-		2011-02-04 12:13:00 & B9.5 & 11152 \\ 
-		2011-02-04 17:30:00 & B1.3 & 11152 \\ 
-		2011-02-04 19:30:00 & B6.9 & 11152 \\ 
-		2011-02-05 00:03:00 & B3.6 & 11152 \\ 
-		2011-02-07 10:17:00 & B1.0 & 11153 \\ 
-		2011-02-07 13:31:00 & B1.9 & 11153 \\ 
-		2011-02-08 01:55:00 & B2.0 & 11153 \\ 
-		2011-02-08 06:48:00 & B1.9 & 11153 \\ 
-		2011-02-08 08:17:00 & B1.9 & 11153 \\ 
-		2011-02-08 09:10:00 & B2.4 & 11150 \\ 
-		2011-02-08 10:28:00 & B1.6 & 11153 \\ 
-		2011-02-08 11:34:00 & B1.9 & 11153 \\ 
-		2011-02-08 14:44:00 & B5.0 & 11153 \\ 
-		2011-02-08 18:46:00 & C1.0 & 11153 \\ 
-		2011-02-09 00:08:00 & C1.1 & 11153 \\ 
-		2011-02-09 01:23:00 & M1.9 & 11153 \\ 
-		2011-02-09 05:42:00 & B4.3 & 11157 \\ 
-		2011-02-09 07:23:00 & B3.2 & 11153 \\ 
-		2011-02-09 10:15:00 & B5.4 & 11153 \\ 
-		2011-02-09 16:19:00 & B8.6 & 11153 \\ 
-		2011-02-09 18:59:00 & B2.6 & 11153 \\ 
-		2011-02-09 22:07:00 & B3.3 & 11153 \\ 
-		2011-02-09 22:54:00 & B7.9 & 11153 \\ 
-		2011-02-10 00:00:00 & B6.3 & 11153 \\ 
-		2011-02-10 03:29:00 & B5.4 & 11153 \\ 
-		2011-02-10 04:39:00 & B6.0 & 11153 \\ 
-		2011-02-10 06:20:00 & C1.9 & 11153 \\ 
-		2011-02-10 06:55:00 & C2.0 & 11153 \\ 
-		2011-02-10 09:24:00 & B4.4 & 11153 \\ 
-		2011-02-10 12:28:00 & C4.7 & 11153 \\ 
-		2011-02-10 13:33:00 & C2.6 & 11153 \\ 
-		2011-02-10 14:38:00 & B6.7 & 11156 \\ 
-		2011-02-10 20:49:00 & B5.3 & 11156 \\ 
-		2011-02-12 14:30:00 & C2.6 & 11159 \\ 
-		2011-02-12 19:13:00 & B5.8 & 11160 \\ 
-		2011-02-12 20:23:00 & B8.9 & 11160 \\ 
-		2011-02-13 00:36:00 & B8.5 & 11158 \\ 
-		2011-02-13 05:59:00 & B3.2 & 11160 \\ 
-		2011-02-13 07:25:00 & C1.4 & 11160 \\ 
-		2011-02-13 12:29:00 & C1.1 & 11158 \\ 
-		2011-02-13 13:44:00 & C4.7 & 11158 \\ 
-		2011-02-13 17:28:00 & M6.6 & 11158 \\ 
-		2011-02-14 02:35:00 & C1.6 & 11158 \\ 
-		2011-02-14 04:29:00 & C8.3 & 11158 \\ 
-		2011-02-14 06:51:00 & C6.6 & 11158 \\ 
-		2011-02-14 08:39:00 & C1.8 & 11158 \\ 
-		2011-02-14 11:51:00 & C1.7 & 11158 \\ 
-		2011-02-14 12:41:00 & C9.4 & 11158 \\ 
-		2011-02-14 13:47:00 & C7.0 & 11158 \\ 
-		2011-02-14 17:20:00 & M2.2 & 11158 \\ 
-		2011-02-14 19:23:00 & C6.6 & 11158 \\ 
-		2011-02-14 23:14:00 & C1.2 & 11158 \\ 
-		2011-02-14 23:40:00 & C2.7 & 11158 \\ 
-		2011-02-15 01:44:00 & X2.2 & 11158 \\ 
-		2011-02-15 14:32:00 & C4.8 & 11158 \\ 
-		2011-02-15 18:07:00 & C1.7 & 11158 \\ 
-		2011-02-15 19:30:00 & C6.6 & 11158 \\ 
-		2011-02-15 22:49:00 & C1.3 & 11158 \\ 
-		2011-02-16 01:56:00 & C2.2 & 11158 \\ 
-		2011-02-16 07:35:00 & M1.1 & 11161 \\ 
-		2011-02-16 09:02:00 & C9.9 & 11158 \\ 
-		2011-02-16 10:25:00 & C3.2 & 11158 \\ 
-		2011-02-16 11:58:00 & C1.0 & 11158 \\ 
-		2011-02-16 14:19:00 & M1.6 & 11158 \\ 
-		2011-02-16 15:27:00 & C7.7 & 11158 \\ 
-		2011-02-16 19:29:00 & C1.3 & 11158 \\ 
-		2011-02-16 20:11:00 & C1.1 & 11158 \\ 
-		2011-02-16 23:02:00 & C2.8 & 11158 \\ 
-		2011-02-17 01:41:00 & C6.1 & 11158 \\ 
-		2011-02-17 02:46:00 & C2.3 & 11158 \\ 
-		2011-02-17 04:09:00 & C1.5 & 11158 \\ 
-		2011-02-17 05:33:00 & C1.0 & 11158 \\ 
-		2011-02-17 06:44:00 & C1.2 & 11158 \\ 
-		2011-02-17 08:09:00 & C1.2 & 11158 \\ 
-		2011-02-17 09:24:00 & C1.9 & 11158 \\ 
-		2011-02-17 10:25:00 & C2.6 & 11158 \\ 
-		2011-02-17 12:33:00 & C2.4 & 11158 \\ 
-		2011-02-17 15:49:00 & C1.3 & 11158 \\ 
-		2011-02-18 01:02:00 & C1.7 & 11158 \\ 
-		2011-02-18 03:20:00 & C2.0 & 11161 \\ 
-		2011-02-18 04:44:00 & C4.0 & 11161 \\ 
-		2011-02-18 06:27:00 & C8.5 & 11158 \\ 
-		2011-02-18 09:55:00 & M6.6 & 11158 \\ 
-		2011-02-18 12:59:00 & M1.4 & 11158 \\ 
-		2011-02-18 14:27:00 & C4.0 & 11158 \\ 
-		2011-02-18 14:57:00 & C5.0 & 11158 \\ 
-		2011-02-18 18:13:00 & C3.2 & 11158 \\ 
-		2011-02-19 01:33:00 & C1.3 & 11158 \\ 
-		2011-02-19 02:21:00 & C1.8 & 11158 \\ 
-		2011-02-19 02:56:00 & C3.4 & 11161 \\ 
-		2011-02-19 06:57:00 & C2.6 & 11162 \\ 
-		2011-02-19 07:40:00 & C1.9 & 11158 \\ 
-		2011-02-19 08:00:00 & C8.5 & 11162 \\ 
-		2011-02-19 12:20:00 & C1.1 & 11162 \\ 
-		2011-02-19 14:50:00 & C1.0 & 11162 \\ 
-		2011-02-19 15:24:00 & C1.5 & 11158 \\ 
-		2011-02-19 16:26:00 & C1.9 & 11158 \\ 
-		2011-02-19 16:39:00 & C6.1 & 11158 \\ 
-		2011-02-20 00:46:00 & C1.2 & 11161 \\ 
-		2011-02-20 02:45:00 & C1.4 & 11162 \\ 
-		2011-02-20 03:54:00 & C1.7 & 11161 \\ 
-		2011-02-20 17:46:00 & B6.2 & 11161 \\ 
-		2011-02-20 19:40:00 & B6.8 & 11161 \\ 
-		2011-02-20 23:00:00 & B3.2 & 11161 \\ 
-		2011-02-20 23:31:00 & B5.2 & 11161 \\ 
-		2011-02-21 01:41:00 & B8.8 & 11161 \\ 
-		2011-02-21 02:13:00 & C4.6 & 11158 \\ 
-		2011-02-21 03:10:00 & C1.8 & 11158 \\ 
-		2011-02-21 04:04:00 & C1.5 & 11158 \\ 
-		2011-02-21 05:00:00 & C4.1 & 11158 \\ 
-		2011-02-21 09:01:00 & C2.7 & 11158 \\ 
-		2011-02-21 10:00:00 & C1.8 & 11158 \\ 
-		2011-02-21 18:25:00 & C1.4 & 11161 \\ 
-		2011-02-22 10:33:00 & B6.5 & 11161 \\ 
-		2011-02-22 12:15:00 & B3.5 & 11161 \\ 
-		2011-02-22 14:34:00 & B2.7 & 11161 \\ 
-		2011-02-23 09:35:00 & B3.1 & 11161 \\ 
-		2011-02-23 10:24:00 & B3.7 & 11161 \\ 
-		2011-02-23 11:10:00 & B6.1 & 11161 \\ 
-		2011-02-23 12:15:00 & C1.2 & 11161 \\ 
-		2011-02-24 02:49:00 & B3.9 & 11161 \\ 
-		2011-02-24 07:23:00 & M3.5 & 11163 \\ 
-		2011-02-24 17:12:00 & B8.5 & 11163 \\ 
-		2011-02-25 01:38:00 & B4.8 & 11163 \\ 
-		2011-02-25 03:22:00 & B4.2 & 11163 \\ 
-		2011-02-25 05:15:00 & C1.4 & 11163 \\ 
-		2011-02-25 05:40:00 & C1.6 & 11163 \\ 
-		2011-02-25 10:53:00 & B6.2 & 11164 \\ 
-		2011-02-25 17:18:00 & C1.1 & 11164 \\ 
-		2011-02-25 22:29:00 & B5.2 & 11163 \\ 
-		2011-02-26 00:07:00 & B4.3 & 11164 \\ 
-		2011-02-26 00:54:00 & B9.0 & 11163 \\ 
-		2011-02-26 05:03:00 & B8.9 & 11164 \\ 
-		2011-02-26 07:32:00 & B4.5 & 11164 \\ 
-		2011-02-26 08:09:00 & C1.3 & 11164 \\ 
-		2011-02-26 09:35:00 & B3.7 & 11164 \\ 
-		2011-02-26 14:34:00 & B8.3 & 11163 \\ 
-		2011-02-26 19:20:00 & B3.9 & 11164 \\ 
-		2011-02-26 20:46:00 & B4.3 & 11163 \\ 
-		2011-02-26 23:23:00 & B5.7 & 11164 \\ 
-		2011-02-27 00:41:00 & B7.3 & 11164 \\ 
-		2011-02-27 03:49:00 & C4.2 & 11164 \\ 
-		2011-02-27 05:04:00 & B2.7 & 11164 \\ 
-		2011-02-27 07:55:00 & B2.8 & 11164 \\ 
-		2011-02-27 14:30:00 & B6.1 & 11164 \\ 
-		2011-02-27 15:47:00 & B7.2 & 11164 \\ 
-		2011-02-27 17:14:00 & B2.9 & 11164 \\ 
-		2011-02-27 22:21:00 & B6.8 & 11164 \\ 
-		2011-02-28 01:44:00 & B5.0 & 11164 \\ 
-		2011-02-28 02:10:00 & B5.0 & 11164 \\ 
-		2011-02-28 04:17:00 & B7.9 & 11164 \\ 
-		2011-02-28 05:24:00 & C1.7 & 11164 \\ 
-		2011-02-28 06:30:00 & C1.1 & 11164 \\ 
-		2011-02-28 07:01:00 & C2.0 & 11164 \\ 
-		2011-02-28 07:34:00 & C2.4 & 11164 \\ 
-		2011-02-28 09:38:00 & C1.5 & 11164 \\ 
-		2011-02-28 10:25:00 & B5.5 & 11164
+		\input{tempplotsmean/flarelist.txt}
 	\label{tab:flares}

### 2015-03-11 paper.tex
Some images resized and a few notes added
Changes to introduction

@@
 Possibly add a reference?
-Many studies have been devoted to this topic (eg, \citealt{Korsos2014, Ahmed2011, Bloomfield2012}, etc.), but few have looked at the temperature of the active regions associated with flares before the flare occurs.
+Many studies have been devoted to the topic of flare prediction (eg, \citealt{Korsos2014, Ahmed2011, Bloomfield2012}, etc.), but few have looked at the temperature of the active regions associated with flares before the flare occurs.
 % Possibly cite more papers or a review.
@@
 
-Studying the temperature of the corona is not a new pursuit, but for many years the data were significantly limited.
-Most imagers had either relatively poor spatial resolution or too few wavelength channels to effectively constrain temperature solutions, whereas spectrometers could provide very accurate temperatures but only over very small portions of the corona.
-Imagers and spectrometers also typically had insufficient temporal resolution to investigate any dynamic events in the corona.
-% All three of these sentences are kind of irrelevant and can be condensed, if not removed.
-Recently, however, the very high temporal and spatial resolution of the Atmospheric Imaging Assembly (AIA) on the Solar Dynamics Observatory (SDO) allows us to investigate small-scale and dynamic events anywhere on the solar disk at any time.
-The six Fe-based EUV channels of AIA also provide sufficent constraints to allow a reasonable estimate of coronal temperatures \citep{Guennou2012, Guennou2012a}.
+Studies of coronal temperatures date back several decades. % Stick some references here to early DEM studies
+However, the Atmospheric Imaging Assembly (AIA) \citep{Lemen2011} which began observing the Sun in 2010 allows unprecedented access to observations with very high spatial and temporal resolution.
+This allos us to investigate temperature distributions on small spatial scales with high cadence. % Don't much like this sentence, but oh well
+The six Fe-based EUV channels of AIA also provide greater constraints on temperature solutions than previous coronal imagers \citep{Guennou2012, Guennou2012a}.
 
@@
 
+% X-flare lines should be darker on all these plots
 \begin{figure}
 	\centering
-		\includegraphics[width=0.7\columnwidth]{tempplotsmax/allars.png}
+		\includegraphics[width=\columnwidth]{tempplotsmax/allars.png}
 	\caption{Change in maximum temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
@@
 	\centering
-		\includegraphics[width=0.7\columnwidth]{tempplots_p95/allars.png}
+		\includegraphics[width=\columnwidth]{tempplots_p95/allars.png}
 	\caption{Change in 95th percentile temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
@@
 	\centering
-		\includegraphics[width=0.7\columnwidth]{tempplotsmean/allars.png}
+		\includegraphics[width=\columnwidth]{tempplotsmean/allars.png}
 	\caption{Change in mean temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
@@
 \end{figure}
+% This can go - adjust the text accordingly
 \begin{figure}
 	\centering
-		\includegraphics[width=0.7\columnwidth]{tempplots_p5/allars.png}
+		\includegraphics[width=\columnwidth]{tempplots_p5/allars.png}
 	\caption{Change in 5th percentile temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
@@
 \end{figure}
+% This can go - adjust the text accordingly
 \begin{figure}
 	\centering
-		\includegraphics[width=0.7\columnwidth]{tempplots_min/allars.png}
+		\includegraphics[width=\columnwidth]{tempplots_min/allars.png}
 	\caption{Change in minimum temperature of the corresponding active region plotted for each flare as a function of time before the flare began.

### 2015-03-11 paper.tex
Minor intro edits

@@
 
-Although it is faster than others of its kind, the temperature-calculating method used here requires a very large amount of AIA data, which can take a long time to download process.
-As such this is a preliminary work investigating a relatively small number of flares and the results should not be considered definitive.
-Rather they are a proof of concept.
-They demonstrate the type of study made available by fast temperature analysis of the corona, which has only become possible. % Perhaps some rephrasing here?
+Although it is faster than others of its kind, the temperature-calculating method used here requires a very large amount of AIA data, which can take a long time to download and process.
+As such this is work investigates only a relatively small number of flares and the results should not be considered definitive.
+Rather they are a proof of concept; they demonstrate the type of study made available by fast temperature analysis of the corona, which has only been made possible by the high-quality data provided by AIA.
 

### 2015-03-12 paper.tex
More minor intro edits
References to paper I redone

@@
 Studies of coronal temperatures date back several decades. % Stick some references here to early DEM studies
-However, the Atmospheric Imaging Assembly (AIA) \citep{Lemen2011} which began observing the Sun in 2010 allows unprecedented access to observations with very high spatial and temporal resolution.
+However, the Atmospheric Imaging Assembly (AIA; \cite{Lemen2011}) which began observing the Sun in 2010 allows unprecedented access to observations with very high spatial and temporal resolution.
 This allos us to investigate temperature distributions on small spatial scales with high cadence. % Don't much like this sentence, but oh well
@@
 Although it is faster than others of its kind, the temperature-calculating method used here requires a very large amount of AIA data, which can take a long time to download and process.
-As such this is work investigates only a relatively small number of flares and the results should not be considered definitive.
+As such this work investigates only a relatively small number of flares and the results should not be considered definitive.
 Rather they are a proof of concept; they demonstrate the type of study made available by fast temperature analysis of the corona, which has only been made possible by the high-quality data provided by AIA.
@@
 \subsection{Temperature analysis}
-The core of this analysis is the temperature map method described by \cite{Leonard} (henceforth Paper I).
+The core of this analysis is the temperature map method described by \cite{Leonard} (henceforth Paper I). \defcitealias{Leonard}{Paper I}
 Briefly, this method compares the relative brightnesses in each AIA wavelength channel at a given time and infers the best-fitting temperature from that comparison.
@@
 
-The Paper I method also allows easy `tracking' of solar regions by cropping the temperature map around a given pair of Carrington heliographic coordinates, which rotate at approximately the rate of solar rotation.
+The \citetalias{Leonard} method also allows easy `tracking' of solar regions by cropping the temperature map around a given pair of Carrington heliographic coordinates, which rotate at approximately the rate of solar rotation.
 This tracking is demonstrated in Figures \ref{fig:trackdemo1} and \ref{fig:trackdemo2}, each of which shows a cropped region of an AIA 17.1nm image containing active region AR11158, the corresponding temperature map and a larger 17.1nm image showing the location of the region in the corona.
@@
 \subsection{Active region analysis}
-The temperature map method described in Paper I was used to investigate the temperatures of the active regions associated with flares which occured during February 2011. % And March, hopefully
+The temperature map method described in citetalias{Leonard} was used to investigate the temperatures of the active regions associated with flares which occured during February 2011.
+% And March, hopefully
 This month was chosen because several flares occured during this time with a wide range of peak fluxes. % These months
@@
 Non-flaring active regions should also be taken into account and compared against the results presented here.
-However, this work does demonstrate that it is now possible to study temperature distributions of the corona in high resolution and on short timescales using fast temperature analysis tools such as the one described in Paper 1.
+However, this work does demonstrate that it is now possible to study temperature distributions of the corona in high resolution and on short timescales using fast temperature analysis tools such as the one described in \citetalias{Leonard}.
 

### 2015-03-12 paper.tex
References to paper I redone minus brainfart

@@
 \subsection{Active region analysis}
-The temperature map method described in citetalias{Leonard} was used to investigate the temperatures of the active regions associated with flares which occured during February 2011.
+The temperature map method described in \citetalias{Leonard} was used to investigate the temperatures of the active regions associated with flares which occured during February 2011.
 % And March, hopefully

### 2015-03-12 paper.tex
Pointless plots removed and relevant changes to text

@@
 \section{Results}
-\subsection{Temperature change over time}
-Figures \ref{fig:allars_max}, \ref{fig:allars_p95}, \ref{fig:allars_mean}, \ref{fig:allars_p5} and \ref{fig:allars_min} show how the temperature properties of the active region changed during the 30 minutes preceding each flare.
+\subsection{Temperature change over time} \label{sec:temps_v_time}
+Figures \ref{fig:allars_max} - \ref{fig:allars_mean} show how the temperature properties of the active region changed during the 30 minutes preceding each flare.
 All of the flares studied are plotted in each of these figures so that any changes common to many flares can be easily noticed.
-The maximum, 95th percentile, mean, 5th percentile and minimum are plotted in figures \ref{fig:allars_max}, \ref{fig:allars_p95}, \ref{fig:allars_mean}, \ref{fig:allars_p5} and \ref{fig:allars_min} respectively.
-In each figure, the top panels show the variation of the relevant parameter's value with time, the middle panels show the running difference and the bottom panes show the difference from the value at the start time of the flare.
-B and C class flares are plotted in the panels on the left, while M and X class flares are shown on the right.
+The maximum, 95th percentile and mean temperatures are plotted in figures \ref{fig:allars_max}, \ref{fig:allars_p95} and \ref{fig:allars_mean} respectively.
+In each figure, B, C, M and X class flares are plotted separately in the panels from left to right respectively.
 
@@
 
-% Description of plots for 5
-The 5th percentile temperature varies very little, both from region to region and over the time investigated.
-All active regions had a temperature of either log(T) = 5.85 or log(T) = 6.16, with a few regions switching between the two values.
-Regions which produced M and X class flares showed no signs of heating to the higher temperature, staying at a constant log(T) = 5.85 for the duration.
-
-% Description of plots for minimum
-From Figure \ref{fig:allars_min} it appears that the minimum temperature was constant throughout the 30 minutes before the flare for almost every active region.
-One or two active regions which produced C class flares show small dips in the minumim temperature, while all other active regions remain constant at log(T) = 5.85.
+% Description of results for p5 and min
+The 5th-percentile and minimum values of the temperature maps showed very little variation for all active regions.
+The 5th-percentile temperature was either log(T) = 5.85 or log(T) = 6.16 for all regions, with a few switching between the two values during the 30-minute period.
+Similarly, the minimum temperature of all active regions was either log(T) = 5.79, log(T) = 5.80 or log(T) = 5.85 throughout the pre-flare period.
+These temperatures showed no variation with the class of the associated flare.
+Plots of these results are not shown here.
 
@@
 \end{figure}
-% This can go - adjust the text accordingly
-\begin{figure}
-	\centering
-		\includegraphics[width=\columnwidth]{tempplots_p5/allars.png}
-	\caption{Change in 5th percentile temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
-Plots and colour-coding are the same as in Figure \ref{fig:allars_max}.}
-	\label{fig:allars_p5}
-\end{figure}
-% This can go - adjust the text accordingly
-\begin{figure}
-	\centering
-		\includegraphics[width=\columnwidth]{tempplots_min/allars.png}
-	\caption{Change in minimum temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
-Plots and colour-coding are the same as in Figure \ref{fig:allars_max}.}
-	\label{fig:allars_min}
-\end{figure}
 
@@
 For each temperature parameter, the value for each flare was plotted on a scatter graph against the peak flux of the flare (Figs.
-\ref{fig:allflares_max}, \ref{fig:allflares_p95}, \ref{fig:allflares_mean}, \ref{fig:allflares_p5} and \ref{fig:allflares_min}).
+\ref{fig:allflares_max}, \ref{fig:allflares_p95}, \ref{fig:allflares_mean}).
 This was done for four times in each case: 30 minutes before the flare start time, 10 minutes before, 1 minute before and at the flare start time.
@@
 
-% Description of plots for 5
-The 5th pecentile temperatures of the active regions were found to be grouped into to distinct temperatures, with no apparent dependence on flux.
-A few active regions heat or cool over the time studied, but most remain the same temperature throughout.
-The hotter of the temperatures found was only present in active regions corresponding to B and C class flares, as can also be seen in Figure \ref{fig:allars_p5}.
-
-% Description of plots for minimum
-Figure \ref{fig:allflares_min} shows that all active regions studied had a minimum temperature of log(T) = 5.85 regardless of the flux of the flare produced.
-All active regions appear to remain a constant temperature throughot the time studied.
+% Description of plots for p5 and min
+As described in Section \ref{sec:temps_v_time}, the 5th-percentile and minimum temperatures showed very little variation, both over time and between active regions.
+These values are therefore not shown here since they reveal no useful information.
 
@@
 \end{figure}
-\begin{figure}
-	\centering
-		\includegraphics[width=0.9\columnwidth]{tempplots_p5/allflares.png}
-	\caption{Scatter graph of flare peak flux against 5th percentile temperature of the corresponding active regions for the same four times as in Figure \ref{fig:allflares_max}.}
-	\label{fig:allflares_p5}
-\end{figure}
-\begin{figure}
-	\centering
-		\includegraphics[width=0.9\columnwidth]{tempplots_min/allflares.png}
-	\caption{Scatter graph of flare peak flux against minimum temperature of the corresponding active regions for the same four times as in Figure \ref{fig:allflares_max}.}
-	\label{fig:allflares_min}
-\end{figure}
 
@@
 
-Figures \ref{fig:allars_max} - \ref{fig:allars_min} show that there is no clear trend in any of the temperature parameters investigated before flares occur.
+Figures \ref{fig:allars_max} - \ref{fig:allars_mean} show that there is no clear trend in any of the temperature parameters investigated before flares occur.
 However, this study only looks at quite a short amount of time before flares; an investigation into longer-term temperature distributions may yield better results.

### 2015-03-12 paper.tex
Figure captions adjusted for new figure layouts

@@
 	\caption{Change in maximum temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
-Top: maximum temperature against time.
-Middle: running difference of maximum temperature.
-Bottom: difference of maximum temperature from maximum temperature at flare start time.
-Left: B and C class flares, denoted by orange and yellow lines, respectively.
-Right: M and X class flares, denoted by red and orange lines, repectively.}
+		Flares are separated by class, with flare peak flux increasing from left to right.}
 	\label{fig:allars_max}
@@
 	\caption{Change in 95th percentile temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
-Plots and colour-coding are the same as in Figure \ref{fig:allars_max}.}
+		Plots are the same as in Figure \ref{fig:allars_max}.}
 	\label{fig:allars_p95}
@@
 	\caption{Change in mean temperature of the corresponding active region plotted for each flare as a function of time before the flare began.
-Plots and colour-coding are the same as in Figure \ref{fig:allars_max}.}
+		Plots are the same as in Figure \ref{fig:allars_max}.}
 	\label{fig:allars_mean}
@@
 The red and blue arrows indicate the amount by which the temperature of each active region rose or fell respectively since the time of the previous plot.
-In each plot the dashed lines indicate the lower thresholds for A, B, C, M and X class flares.}
+In each plot the dashed lines indicate the lower X-ray flux thresholds for A, B, C, M and X class flares.}
 	\label{fig:allflares_max}

### 2015-03-12 paper.tex
Edits to include March

@@
 \subsection{Active region analysis}
-The temperature map method described in \citetalias{Leonard} was used to investigate the temperatures of the active regions associated with flares which occured during February 2011.
-% And March, hopefully
-This month was chosen because several flares occured during this time with a wide range of peak fluxes. % These months
-The flares detected included many small flares (B and C class) as well as several larger M class flares and a single X class flare. % Double check these numbers to include March
+The temperature map method described in \citetalias{Leonard} was used to investigate the temperatures of the active regions associated with flares which occured during February and March 2011.
+These months were chosen because several flares occured during this time with a wide range of peak fluxes.
+The flares detected included many small flares (B and C class) as well as several larger M class flares and two X class flares.
 
 For each flare event investigated, a temperature map was calculated for a 150 x 150 arcsec area around the corresponding active region at 1-minute intervals for the 30 minutes preceding the start of the flare.
-% Double check temperature map size
 The maximum, 95th percentile, mean, 5th percentile and minimum temperatures were then calculated for each temperature map for each flare in order to compare if and how the bulk temperature of the active regions changed before the flare.
@@
 \begin{longtable}{c|c|c}
-	\caption{Start times and associated active regions of solar flares studied during 2011-02.}\\ % And March
+	\caption{Start times and associated active regions of solar flares studied during 2011-02 and 2011-03.}\\
 		Date and time & GOES class & NOAA Active region \\

### 2015-03-17 paper.tex
Minor edits based on Huw's suggestions

@@
 However, the Atmospheric Imaging Assembly (AIA; \cite{Lemen2011}) which began observing the Sun in 2010 allows unprecedented access to observations with very high spatial and temporal resolution.
-This allos us to investigate temperature distributions on small spatial scales with high cadence. % Don't much like this sentence, but oh well
-The six Fe-based EUV channels of AIA also provide greater constraints on temperature solutions than previous coronal imagers \citep{Guennou2012, Guennou2012a}.
+This allows investigation of temperature distributions on small spatial scales with high cadence. % Don't much like this sentence, but oh well
+The six Fe-based EUV channels of AIA also provide greater constraints on temperature than previous coronal imagers \citep{Guennou2012, Guennou2012a}.
 
@@
 The aim is to search for a common signature of flare activity in these temperature distributions before flares occur, which, if found, could form the basis of a flare prediction algorithm.
-To achieve this, we look at temperature distributions of the active regions over the 30 minutes before a flare occurs, and we also directly compare the temperatures of the corresponding active regions at several different times before the flares.
+
+%===========================================================================
+\section{Method}
+This investigation looks at temperature distributions of active regions over the 30 minutes before a flare occurs.
+We also directly compare the temperatures of the corresponding active regions at several different times before the flares.
 
@@
 
-%===========================================================================
-\section{Method}
 \subsection{Temperature analysis}
@@
 This tracking is demonstrated in Figures \ref{fig:trackdemo1} and \ref{fig:trackdemo2}, each of which shows a cropped region of an AIA 17.1nm image containing active region AR11158, the corresponding temperature map and a larger 17.1nm image showing the location of the region in the corona.
+Note that the small, bright loops in the centre of the active region are highlighted in red, indicating temperatures of up to $log(T) \sim 6.3$, while some larger, fainter loops around the edges are at temperatures of around $log(T) \sim 6.15$.
+These temperatures are consistant with values found by other authors for active region loops. % Reference the shit out of that comment.
 
@@
 \begin{longtable}{c|c|c}
-	\caption{Start times and associated active regions of solar flares studied during 2011-02 and 2011-03.}\\
+	\caption{Start times and associated active regions of solar flares studied between 2011/02/01 and 2011/03/31.}\\
 		Date and time & GOES class & NOAA Active region \\
@@
 \section{Discussion and conclusions}
-From this study, it appears that there is no clear link between solar flares and coronal temperatures.
+From this study, it appears that there is no clear link between solar flares and the evolution of active region temperatures prior to flaring.
 This is probably mostly due to the relatively small number of flares studied - a much larger sample size would have to be used to properly determine any link or lack thereof.
-In particular, this study only included a single X class flare, which as the most energetic are the kind we would most wish to predict.
-Future works should therefore aim to consider more large flares.
+In particular, this study only included a single X class flare, which are the most energetic and the kind we would most wish to predict.
+Future works should therefore aim to consider larger flares.
 Non-flaring active regions should also be taken into account and compared against the results presented here.
@@
 	This research has made use of SunPy, an open-source and free community-developed solar data analysis package written in Python \citep{Mumford2013}.
+	AIA images courtesy of NASA/SDO and the AIA science team.
 \end{acknowledgements}

### 2015-03-20 plotflares4.py
plotflares rehashed

@@ -12,6 +12,7 @@ import matplotlib.pyplot as plt
 import matplotlib.cm as cmx
 import matplotlib.colors as colours
 from sunpy import wcs
+from sunpy.map import Map
 from sunpy.net import hek
 from sunpy.time import parse_time as parse
 from sunpy.time.timerange import TimeRange as tr
@@ -66,7 +67,7 @@ parind = allpars.index(parameter)
 savedir = "/imaps/holly/home/ajl7/tempplots_{}/".format(parameter.replace(' ', '_'))
 
 start = parse('2011-02-01')
-end = parse('2011-04-01')
+end = parse('2011-02-15')
 
 client = hek.HEKClient()
 flares = client.query(hek.attrs.Time(start, end),
@@ -121,9 +122,12 @@ axr4.set_xlabel("Time (minutes)")"""
 cmap = cm = plt.get_cmap('afmhot')
 cNorm  = colours.Normalize(vmin=0, vmax=1)
 scalarMap = cmx.ScalarMappable(norm=cNorm, cmap=cmap)
-flarecolours = {'A': 0.2, 'B': 0.35, 'C': 0.5, 'M': 0.65, 'X': 0.8}
+flarecolours = {'A': 0.2, 'B': 0.3, 'C': 0.4, 'M': 0.5, 'X': 0.6}
+
+allars_hist = np.zeros((141, 30))
 
 for flare in flares:
+  if flare['fl_goescls'] != "M6.6": continue
   try:
     flaretime = parse(flare['event_starttime'])
     starttime = flaretime-dt.timedelta(hours=0.5)
@@ -149,9 +153,12 @@ for flare in flares:
     times = [time.start() for time in timerange.split(ntimes)]
     
     data_dir = '/imaps/sspfs/archive/sdo/aia/activeregions/AR{}/data/'.format(flare['ar_noaanum'])
-    maps_root = '/imaps/sspfs/archive/sdo/aia/activeregions/AR{}/images/'.format(flare['ar_noaanum'])
+    #maps_root = '/imaps/sspfs/archive/sdo/aia/activeregions/AR{}/images/'.format(flare['ar_noaanum'])
+    maps_root = '/imaps/holly/home/ajl7/AR-tmaps/AR{}/'.format(flare['ar_noaanum'])
     params_dir = '/imaps/holly/home/ajl7/AR_temp_params/AR{}/'.format(flare['ar_noaanum'])
[…]
